---
title: "Ploidy"
author: "Jonathan"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Install/load 'conumee' package for CNV and 'minfi' for reading .idat files:

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE)){
    install.packages("BiocManager")
}
if (!requireNamespace("minfi", quietly = TRUE)){
    BiocManager::install("minfi")
}

if (!requireNamespace("conumee", quietly = TRUE)){
    BiocManager::install("conumee")
}
library("minfi")
library("conumee")
```


2. Read the .idat files using the 'minfi' package:

```{r}
base_path <- "path/to/your/idat/files"
targets <- read.metharray.sheet(base_path)
RGset <- read.metharray.exp(targets = targets)
```

3. Preprocess the data and obtain the log R ratio (LRR) values:

```{r}
Mset <- minfi::preprocessQuantile(RGset, normalize = "controls")
LRR_matrix <- getLogRatio(Mset)
```

4. Create a conumee object containing the LRR values and other necessary information:

```{r}
my_conumee <- createConumeeObject(LRR_matrix, RGset)
```

5. Preprocess and normalize the LRR values using the 'conumee' package:

```{r}
my_conumee <- preprocessLRR(my_conumee)
my_conumee <- normalizeLRR(my_conumee)
```

6. Perform segmentation to identify genomic regions with different copy numbers:

```{r}
segmented_data <- segment(my_conumee)
```

7. To estimate ploidy, you can calculate the median of the segmented LRR values across the genome for each sample. The median LRR value can be used to infer ploidy by assuming a diploid (2N) baseline:

```{r}
ploidy_estimates <- apply(segmented_data$LRR, 2, median)
ploidy_values <- 2 * 2 ^ ploidy_estimates
```

The 'ploidy_values' object will contain the ploidy estimates for each sample in your dataset.

