---
output:
  html_document: 
    self_contained: yes
    code_download: yes
    toc_depth: 2
---

```{r setup, fig.keep='all', fig.path="figures/", include=FALSE, error=FALSE}
gb <- globalenv(); assign("gb", gb)
gitUrl <- "https://raw.githubusercontent.com/NYU-Molecular-Pathology/Methylation/main/Research"
devtools::source_url(file.path(gitUrl, "SetupMethKnit.R")); gb$loadHtmlTag()
targets <- gb$GenerateTargets(gb)
```

```{css, label='css-code', echo=FALSE, code=readLines(gb$cssLink)}
```

---
title: "`r gb$htmlTitle`"
author: "`r gb$yourName`"
date: "`r gb$yourDate`"
---

```{r, Project-Info, child='params/about.Rmd', include=TRUE, cache=FALSE}
```

# Input Sample Sheet Information
```{r, Samplesheet, out.width='60%', echo=FALSE, message=FALSE, results='asis'}
gb$makeDt(targets, gb, T); gb$htmlClose()
```

## Sample Types from Sample Sheet Above
```{r, sam-type, echo=FALSE, out.width='25%', results='asis', fig.align='left'}
gb$MsgSamFreq(targets, gb)
```

```{r, Load-RGSet-and-Betas, echo=FALSE, include=FALSE}
RGSet <- gb$GetRgsetDat(csvPath = gb$samsheet, gb)
targets <- gb$MatchRGtargets(RGSet, targets, gb$samsheet)
betas <- gb$cleanRawProbes(RGSet, targets, gb)
theMissing <- gb$dropBadQc(targets, betas, gb$samsheet)
RGSet <- gb$cleanRgset(RGSet, gb$col_sentrix, betas)
gb$mSetSq.beta <- gb$GetMsetSq(RGSet, targets, gb$mbfile)
gb$LoopSuperviseCategory(gb, RGSet, betas)
```

# MDS Plots {.tabset}
```{r, MDS-plots, opts.label='mdsopts'}
gb$MakeHideButton("MDSdata")
gb$LoopPlotMds(gb$mSetSq.beta, targets, gb$selectedVars, gb$topN)
gb$MessageBatchMix(targets, gb)
gb$ShowAnyMissed(gb); gb$htmlClose()
```

# All Groups Unsupervised TSNE
```{r, Unsuper-TSNE, opts.label='tsnechunk', fig.path=tsneOutU}
gb$MakeHideButton("unsupertsne")
targets1 <- gb$SubsetTargets(targets, gb$variable_to_filter)
gb$run_tsne_plots(targets1, betas, gb, shapeVariable = gb$col_shapes)
gb$CatShapeColor(tbset = FALSE)
gb$run_tsne_plots(targets1, betas, gb, shapeVariable = gb$col_Grouping)
gb$htmlClose()
```

# DMP Supervised TSNE
```{r, Supervised-TSNE, opts.label='tsnechunk', fig.path=tsneOutS}
gb$MakeHideButton("supertsne")
gb$LoopSupervisedPlots(targets, gb); gb$htmlClose()
```

# Unsupervised HeatMaps
<hr style="border:2px solid gray">
```{r, HM-unsupervised-anno, echo=FALSE, include=FALSE, eval=gb$genHeatMaps}
gb$LoadHeatMapLibs()
hmPlotData <- gb$GetHeatMapData(targets, betas, RGSet, gb)
```

## All groups HeatMap (Unsupervised) {.tabset}
```{r, Unsuper-HM, opts.label='hmopts', fig.path=hmOutU, eval=gb$genHeatMaps}
gb$MakeHideButton("uheatmaps")
gb$LoopPrintHeatMap(gb, unBetas = hmPlotData$unBetas, ha = hmPlotData$ha)
gb$htmlClose()
```

# Supervised HeatMaps
<hr style="border:2px solid gray">
```{r, HM-super, echo=FALSE, fig.keep='all', include=FALSE, eval=gb$superHeat}
gb$GetSuperHmData(gb, targets, RGSet)
```

## All groups HeatMap (Supervised) {.tabset}
```{r, supervise-HM, opts.label='hmopts', fig.path = hmOutS, eval=gb$superHeat}
gb$MakeHideButton("sheatmaps")
gb$LoopSupervisedHm(gb)
gb$htmlClose()
```

```{r, label='segfile-save', opts.label='cn_opts1', eval=gb$genCNchunk}
gb$cnData <- gb$grabClusterDat(gb$seg_clust_file, gb$segFile, targets, gb$idatPath)
gb$loadHtmlTag()
```

# Copy Number Variation
<hr style="border:2px solid gray">
```{r, sam-cnv-save, opts.label='gencnv', include=TRUE, eval=gb$genCNchunk}
gb$MakeHideButton("plaincnv")
gb$LoopSavePlainCNV(targets)
```

```{r, label='CNV-plots', opts.label='cn_opts2', eval=gb$genCNchunk}
gb$SaveLoadCnvs(gb$cnData[, 1:(ncol(gb$cnData))])
if (length(gb$col_samGrp) > 1) {
  gb$GenCNVdataGroupSave(gb$cnData, targets, gb$col_samGrp)
}
gb$htmlClose()
```

```{r, label='cluster profile', opts.label='clustprof', include=TRUE}
if (gb$genPathChunk == TRUE) {
  gb$PrintPathHeader(gb$GroupSubset)
  enrichedData <- gb$GetKeggGeneVals(RGSet, targets, gb$pathwayGrp_Filter, gb)
  gb$geneVals <- enrichedData$geneVals
} else{cat(rep("<br>", 5), sep = "\n"); knitr::knit_exit("</body></html>")}
```

# Pathway Gene HeatMaps
```{r, label='GeneClusterHM', opts.label='pathhm', include=TRUE}
gb$MakeHideButton("PathHeat")
gb$pathWayGenes <- gb$WritePathVals(gb$geneVals, gb$geneListIn)
gb$LoopPathwayHeatMap(gb$pathWayGenes[gb$totPaths,], RGSet, betas, targets)
gb$htmlClose()
```

# Pathway Genes
```{r, label='Top Gene Paths', opts.label='genepath', include=TRUE}
gb$MakeHideButton("PathGenes")
gb$PrintPathways(gb$pathWayGenes)
gb$htmlClose()
```
