---
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: 
    self_contained: yes
    code_download: yes
    theme: cerulean
    toc: yes
    toc_depth: 2
    highlight: tango
    fig_width: 15
    fig_height: 10
editor_options:
  chunk_output_type: console
---

```{r setup, fig.keep='all', fig.path = "figures/", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = TRUE, cache = FALSE)
gb <- globalenv(); assign("gb", gb)
gitUrl <- "https://raw.githubusercontent.com/NYU-Molecular-Pathology/Methylation/main/Research"
devtools::source_url(file.path(gitUrl, "SetupMethKnit.R"))
knitr::opts_knit$set(gb$knitOpt); knitr::opts_chunk$set(gb$knitOpt)
gb$sourceParams(); gb$loadHtmlTag(); gb$assignOpts()
targets <- gb$GenerateTargets(gb); gc(F)
```

---
title: "`r gb$htmlTitle`"
author: "`r gb$yourName`"
---

```{css, echo=FALSE, code=readLines(gb$cssLink)}
```

```{r,label='Project Info', child='./params/about.Rmd', include=TRUE}
```

# Input Sample Sheet Information
```{r, label='Print Samplesheet', out.width='60%', echo=FALSE, message=FALSE, results='asis'}
gb$makeDt(targets, gb, T); gb$htmlClose()
```

## Sample Types from Sample Sheet Above
```{r, label='Count Unique', echo=FALSE, out.width='25%', results='asis', fig.align='left'}
gb$MsgSamFreq(targets, gb)
```

```{r, label='Load RGSet and Betas', echo=FALSE, include=FALSE}
RGSet <- gb$GetRgsetDat(csvPath = gb$samsheet, gb)
targets <- gb$MatchRGtargets(RGSet, targets, gb$samsheet)
betas <- gb$cleanRawProbes(RGSet, targets, gb)
theMissing <- gb$dropBadQc(targets, betas, gb$samsheet)
RGSet <- gb$cleanRgset(RGSet, gb$col_sentrix, betas)
gb$mSetSq.beta <- gb$GetMsetSq(RGSet, targets, gb$mbfile)
gb$LoopSuperviseCategory(gb, RGSet, betas)
```

# MDS Plots {.tabset}
```{r, label='MDS-plots', opts.label='mdsopts'}
gb$MakeHideButton("MDSdata")
gb$LoopPlotMds(gb$mSetSq.beta, targets, gb$selectedVars, gb$topN)
gb$MessageBatchMix(targets, gb)
gb$ShowAnyMissed(gb); gb$htmlClose()
```

# All Groups Unsupervised TSNE
```{r, label='Unsupervised_TSNE', opts.label='tsnechunk', fig.path=tsneOutU, fig.show='hide'}
gb$MakeHideButton("unsupertsne")
targets1 <- gb$SubsetTargets(targets, gb$variable_to_filter)
gb$RunTsneAnalysisAndSavePlots(targets1, betas, gb, shapeVariable = gb$col_shapes)
gb$CatShapeColor(tbset = FALSE)
gb$RunTsneAnalysisAndSavePlots(targets1, betas, gb, shapeVariable = gb$col_Grouping)
gb$htmlClose()
```

# DMP Supervised TSNE
```{r, label='Supervised_TSNE', opts.label='tsnechunk', fig.path=tsneOutS}
gb$MakeHideButton("supertsne")
gb$LoopSupervisedPlots(targets, gb); gb$htmlClose()
```

# Unsupervised HeatMaps
<hr style="border:2px solid gray">
```{r, label='HM-unsupervised-annotations', echo=FALSE, include=FALSE, eval=gb$genHeatMaps}
gb$LoadHeatMapLibs()
hmPlotData <- gb$GetHeatMapData(targets, betas, RGSet, gb)
```

## All groups HeatMap (Unsupervised) {.tabset}
```{r, label='Unsupervised-HM-plot', opts.label='hmopts', fig.path=hmOutU}
gb$MakeHideButton("uheatmaps")
if (gb$genHeatMaps == T) {
  gb$LoopPrintHeatMap(gb, unBetas = hmPlotData$unBetas, ha = hmPlotData$ha,
                      geneNams = gb$addGenesHm, colSplt = gb$colSplitHm, 
                      hideTopAnno = gb$hideTopAnno)
} else{
  cat("No Unsupervised HeatMaps output")
}
gb$htmlClose()
```

# Supervised HeatMaps
<hr style="border:2px solid gray">
```{r, label='HM-supervised-annotations', echo=FALSE, fig.keep='all', fig.path=hmOutS, include=FALSE}
if (gb$supervisedRun == T & gb$genHeatMaps == T) {
  gb$GetSuperHmData(gb, targets, RGSet)
} else{
  cat("No Supervised HeatMaps output")
}
```

## All groups HeatMap (Supervised) {.tabset}
```{r, label='supervised-HM-plot', opts.label='hmopts', fig.path = hmOutS, include=TRUE}
gb$MakeHideButton("sheatmaps")
if (gb$supervisedRun == T & gb$genHeatMaps == T) {
  gb$LoopSupervisedHm(gb)
} else{
  cat("No Supervised HeatMaps output")
}
gb$htmlClose()
```

```{r, label='segfile-generation', opts.label='cn_opts_1', include=FALSE, eval=gb$genCNchunk}
gb$cnData <- gb$grabClusterDat(gb$seg_clust_file, gb$segFile, targets, gb$idatPath)
gb$loadHtmlTag()
```

# Copy Number Variation
<hr style="border:2px solid gray">
```{r, label='sample-cnv-generation', opts.label='gencnv', include=TRUE, eval=gb$genCNchunk}
gb$MakeHideButton("plaincnv")
gb$LoopSavePlainCNV(targets)
```

```{r, label='CNV-plots', opts.label='cn_opts_2', include=TRUE, eval=gb$genCNchunk}
gb$SaveLoadCnvs(gb$cnData[, 1:(ncol(gb$cnData))])

if (length(gb$col_samGrp) > 1) {
  gb$GenCNVdataGroupSave(gb$cnData, targets, gb$col_samGrp)
}
gb$htmlClose()
```

```{r, label='cluster profile', opts.label='clustprof', include=TRUE}
if (gb$genPathChunk == TRUE) {
  gb$PrintPathHeader(gb$GroupSubset)
  enrichedData <- gb$GetKeggGeneVals(RGSet, targets, nameGrp = gb$pathwayGrp_Filter, gb = gb)
  gb$geneVals <- enrichedData$geneVals
} else{
  cat(rep("<br>", 5), sep = "\n")
  knitr::knit_exit("</body></html>")
}
```

# Pathway Gene HeatMaps
```{r, label='GeneClusterHM', opts.label='pathhm', include=TRUE}
gb$MakeHideButton("PathHeat")
gb$pathWayGenes <- gb$WritePathVals(gb$geneVals, gb$geneListIn)
gb$LoopPathwayHeatMap(gb$pathWayGenes[gb$totPaths,], RGSet, betas, targets)
gb$htmlClose()
```

# Pathway Genes
```{r, label='Top Gene Paths', opts.label='genepath', include=TRUE}
gb$MakeHideButton("PathGenes")
gb$PrintPathways(gb$pathWayGenes)
gb$htmlClose()
```
