---
author: "Your Name"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: 
    code_download: yes
    theme: cerulean
    toc: yes
    toc_depth: 2
    highlight: tango
    fig_width: 15
    fig_height: 10
editor_options:
  chunk_output_type: console
---

```{r setup, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.keep='all', fig.path = "figures/", include=FALSE}
gb <- globalenv(); assign("gb", gb)
gitUrl <- "https://raw.githubusercontent.com/NYU-Molecular-Pathology/Methylation/main/Research"
devtools::source_url(file.path(gitUrl, "SetupMethKnit.R"))
knitr::opts_knit$set(gb$knitOpt); knitr::opts_chunk$set(gb$knitOpt)
gb$sourceParams(); gb$loadHtmlTag()
targets <- gb$GenerateTargets(gb)
```
---
title: "`r paste(gb$htmlTitle)`"
---
```{css, echo=FALSE,code=readLines("https://raw.githubusercontent.com/NYU-Molecular-Pathology/Methylation/main/Research/Research.css")}
```
```{r,label='Project Info', child='./params/about.Rmd', include=TRUE}
```
# Input Sample Sheet Information

<button class="btn btn-primary" data-toggle="collapse" data-target="#SampleData">Show/Hide</button>
::: {#SampleData .collapse style="width:100%; height:auto; margin: 0px;"}
```{r, label='Print Samplesheet', out.width='60%', echo=FALSE, message=FALSE}
gb$makeDt(targets, gb) # Prints out the samplesheet data in an html table
```
:::

## Sample Types from Sample Sheet Above

```{r, label='Count Unique', echo=FALSE, out.width='25%', results='asis', fig.align='left'}
gb$MsgSamFreq(targets, gb)
```

```{r, label='Load RGSet and Betas', echo=FALSE, include=FALSE}
RGSet <- gb$GetRgsetDat(csvPath = "samplesheet.csv", gb)
targets <- gb$MatchRGtargets(RGSet, targets, gb$samsheet)
betas <- gb$cleanRawProbes(RGSet, targets, gb)
targets <- gb$MatchBetas2Targets(targets, betas)
theMissing <- gb$dropBadQc(targets, betas) # Drop low-quality probe samples (exports csv)
targets <- gb$getTargCsv(gb$samsheet)
RGSet <- gb$cleanRgset(RGSet, gb$col_sentrix, betas)
gb$mSetSq.beta <- gb$GetMsetSq(RGSet, targets, gb$mbfile)
if(gb$supervisedRun){
    for(i in 1:length(gb$selectedVars)){
        superbetas <- gb$loadSupervise(RGSet, betas, gb, gb$selectedVars[i], dmpTyp = "categorical")
        varName <- paste0("superbetas", i)
        assign(x = varName, value = superbetas, envir = gb)
    }
}
```

# MDS Plots {.tabset}

```{r, label='MDS-plot1', echo=FALSE, fig.height=7, fig.width=12, out.width='100%', dpi=350, fig.keep='all', fig.path = "figures/mds/", include=TRUE}
gb$LoopPlotMds(gb$mSetSq.beta, targets, gb$selectedVars, gb$topN)
gb$MessageBatchMix(targets, gb)
gb$ShowAnyMissed(gb)
```

# All Groups Unsupervised TSNE
```{r ,label='TSNE Unsupervised2', echo=FALSE, error=FALSE, dpi=350, out.height="650px", out.width="3650px", results='asis', fig.path="figures/tsne/", fig.keep='all'}
targets1 <- gb$SubsetTargets(targets, gb$variable_to_filter)
tnseHead <- gb$GetColorShape(gb$col_samGrp, gb$col_shapes)

gb$GetCatHeader(tnseHead)
gb$GenerateUnsuperTsne(targets1, betas, gb)

gb$GetCatHeader(NULL, FALSE)

tnseHead <- gb$GetColorShape(gb$col_samGrp, gb$col_Grouping)
gb$GetCatHeader(tnseHead)
targets1 <- gb$SubsetTargets(targets)
gb$GenerateUnsuperTsne(targets1, betas, gb, shapeVariable = gb$col_Grouping)
cat('\n\n')
```

# DMP Supervised TSNE

```{r, label='TSNE Supervised2', echo=FALSE, error=FALSE, dpi=350, out.height="650px", out.width="3650px", results='asis', fig.path="figures/tsne/", fig.keep='all'}
if (gb$supervisedRun) {
    targets1 <- gb$SubsetTargets(targets, gb$variable_to_filter)
    for(i in 1:length(gb$selectedVars)){
        tnseHead <- gb$GetColorShape(gb$col_samTypes, gb$samGroup)
        gb$GetCatHeader(tnseHead)
        gb$superbetas <- eval(parse(text = paste0("gb$superbetas", i)))
        gb$GenerateUnsuperTsne(targets1, betas = gb$superbetas, gb, colorVariable = gb$selectedVars[i],
                               shapeVariable = gb$samGroup, isSuper = T)
        cat("\n\n")
    }
} else {cat("No supervised analysis output")}
```

# HeatMaps
<hr style="border:4px solid gray">

```{r, label='HM-unsupervised-annotations', echo=FALSE, include=FALSE}
gb$LoadHeatMapLibs()
hmPlotData <- gb$GetHeatMapData(targets, betas, RGSet, gb)
```

## All groups HeatMap (Unsupervised) {.tabset}

```{r, label='Unsupervised-HM-plot', echo=FALSE, fig.width=18, fig.height=22, dpi=350, fig.keep='all', results='asis', fig.path = "figures/heatmaps/"}
hm.db <- gb$LoopPrintHeatMap(hmPlotData$unBetas, hmPlotData$ha, geneNams = gb$addGenesHm, colSplt = 5)
gb$LoopSaveHm(hm.db, gb$varProbes)
```

```{r, label='HM-unsupervised-annotations2', echo=FALSE, fig.keep='all', fig.path = "figures/heatmaps/", include=FALSE}
hmPlotData <- gb$GetHeatMapData(targets, gb$superbetas, RGSet, gb)
```

# Supervised HeatMaps

## All groups HeatMap (Supervised) {.tabset}

```{r, label='supervised-HM-plot', echo=FALSE, fig.width=18, fig.height=22, dpi=350, fig.keep='all', results='asis', fig.path = "figures/heatmaps/"}
hm.db <- gb$LoopPrintHeatMap(hmPlotData$unBetas, hmPlotData$ha, geneNams = gb$addGenesHm, colSplt = 5)
gb$LoopSaveHm(hm.db, gb$varProbes)
```

# Copy Number Plots

```{r, label='segfile-generation', echo=FALSE, fig.height=8, fig.width=15, fig.asp=0.75, include=FALSE, fig.path = "figures/cnv/"}
if (gb$generateCNVchunk){
    gb$writeSegTab(gb$segFile, targets, idatPath = file.path(getwd(), "idats"))
    cnData <- gb$grabClusterDat(gb$seg_clust_file, gb$segFile)
    gb$loadHtmlTag()
} else{
    cat("No CNV analysis output")
}
```

# Copy Number Variation
```{r, label='sample-cnv-generation', echo=FALSE, fig.keep='all', fig.path="figures/cnv/", results='asis', include=TRUE}
if (gb$generateCNVchunk){gb$LoopSavePlainCNV(targets)}else{cat("No CNV analysis output")}
```

## Sample `r I(as.character(gb$col_samGrp))` Groups CNV Frequency {.tabset}

```{r, label='CNV-plots', echo=FALSE, error=FALSE, fig.keep='all', fig.path='figures/cnv/', fig.show='asis', fig.height=10, fig.width=16, dpi=300, include=TRUE, out.width='100%', results='asis'}
if (gb$generateCNVchunk){
gb$SaveLoadCnvs(cnData[, 1:(ncol(cnData))], plotName = "All", "All")
gb$GenCNVdataGroupSave(cnData, targets, gb$col_samGrp)
} else{
    cat("No CNV analysis output")
}
if (gb$genPathwaychunk) {gb$PrintPathHeader(gb$GroupSubset)}else{knitr::knit_exit()}
```

```{r, label='cluster profile', echo=FALSE, fig.path = "figures/cluster/", dpi=300, fig.height=5, fig.width=8, out.width='800px', include=TRUE}
enrichedData <- gb$GetKeggGeneVals(RGSet, targets, nameGrp = gb$pathwayGrp_Filter, gb = gb)
gb$geneVals <- enrichedData$geneVals
```

# Pathway Gene HeatMaps

<button class="btn btn-primary" data-toggle="collapse" data-target="#PathHeat">Show/Hide</button>
::: {#PathHeat .collapse style="width:100%; height:auto; margin: 0px;"}
```{r, label='GeneClusterHeatMap', echo=FALSE, fig.path="figures/heatmaps/", fig.align='left', fig.width=18, fig.height=22, dpi=350, fig.keep='all', include=TRUE, results='asis'}
gb$pathWayGenes <- gb$WritePathVals(gb$geneVals, gb$geneListIn)
gb$LoopPathwayHeatMap(gb$pathWayGenes[1:3,], RGSet, betas, targets)
```
:::

# Pathway Genes
```{r, label='Top pathways gene', echo=FALSE, fig.height=7, fig.width=12, out.width='100%', dpi=350, fig.keep='all', fig.path = "figures/pathway/", include=TRUE, results='asis'}
gb$PrintPathways(gb$pathWayGenes)
```
