---
title:  "Methylation Analysis"
author: "Jonathan Serrano"
date: "`r format(Sys.time(),'%d %B, %Y')`"
output:
  html_document: 
    code_download: yes
    theme: cerulean
    toc: yes
    highlight: tango
    fig_width: 15
    fig_height: 10
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.keep='all', fig.path = "figures/", error=FALSE}
gb <- globalenv(); assign("gb", gb)
if (!require("devtools")) {install.packages("devtools", dependencies = T, ask = F)}
gitUrl <- "https://raw.githubusercontent.com/NYU-Molecular-Pathology/Methylation/main/Research"
devtools::source_url(file.path(gitUrl,"SetupMethKnit.R"))
knitr::opts_knit$set(gb$knitOpt); knitr::opts_chunk$set(gb$knitOpt)
gb$sourceParams(); gb$setKnitDir(gb$runDir); stopifnot(gb$runDir == getwd())
targets <- gb$sanitizeSheet(gb$inputFi, gb$samsheet) # Drop commas in xlsx sheet
targets <- gb$ModifyTargetColumns(targets, gb)
if(is.null(gb$col_sentrix)){gb$col_sentrix <- "SentrixID_Pos"}
```

<style>.myTable td {padding: 3px}
.myTable tbody tr:nth-child(odd){background-color: #ADD8E6;}
table {white-space: nowrap;}</style>

```{r,label='Project Info', child='./parameters/about.Rmd'}
```

# Input Sample Sheet Information
<div style = "width:100%; height:auto; margin: 0px;">
```{r, label='Print Samplesheet', out.width='60%', echo=FALSE, include=TRUE, message=FALSE}
gb$makeDt(targets, gb) # Prints out the samplesheet data in an html table
```
</div>

## Sample Types from Sample Sheet Above
```{r, label='Count Unique', out.width='25%', echo=FALSE, include=TRUE, results='asis'}
gb$PrintSamTypes(targets, gb$col_samTypes)
if(gb$col_samGrp != gb$col_samTypes){gb$PrintSamTypes(targets, gb$col_samGrp)}
gb$PrintSamTypes(targets, gb$col_arrayType)
gb$MsgNoobInfo(gb$getNoob)
```

```{r, label='Load RGSet and Betas', include=FALSE, echo=FALSE, message=FALSE}
RGSet <- gb$GetRgsetDat(csvPath = "samplesheet.csv", gb) 
targets <- gb$MatchRGtargets(RGSet, targets, gb$samsheet)
betas <- gb$cleanRawProbes(RGSet, targets, gb)
theMissing <- gb$dropBadQc(targets, betas) # Drop low-quality probe samples (exports csv)
targets <- gb$getTargCsv(gb$samsheet)
RGSet <- gb$cleanRgset(RGSet, gb$col_sentrix, betas)

if (gb$supervisedRun == T) {superbetas <- gb$loadSupervise(RGSet, betas, gb$supbetaOut, gb$varProbes)}

gb$mSetSq.beta <- gb$GetMsetSq(RGSet, targets, gb$mbfile)
```

```{r, label='MDS-plot1', echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, fig.width=6, out.width='90%', dpi=300, fig.keep='all', fig.path = "figures/mds/"}
gb$LoopPlotMds(gb$mSetSq.beta, targets, gb$selectedVars, gb$topN)
```

```{r, label='Message Missing and Params', out.width='50%', echo=FALSE}
gb$printMissing(theMissing, gb)
gb$ShowAnyMissed(gb)
gb$MessageBatchMix(targets, gb)
```

<p><hr class='solid' size="8" width="90%" color="seagreen"> </hr></p>

# TSNE Plots
```{r, label='ggplotly loader', include=FALSE, cache=FALSE, echo=FALSE}
library("ggplot2")
gb$loadHtmlTag()
set.seed(1234)
```

# All Groups Unsupervised TSNE 

## `r I(as.character(gb$tsneHead1))` {.tabset}
```{r, label='TSNE Unsupervised1', echo=FALSE, error=FALSE, fig.keep='all', message=FALSE, warning=FALSE, cache=FALSE, dpi=300, out.height="650px", out.width="3600px", results='asis', fig.path="figures/tsne/"}
targets <- gb$colorTargets(targets, gb$col_samTypes)
targets1 <- gb$SubsetTargets(targets)
samShapesCol = gb$col_samTypes

gb$subsetBetas(
  targFilter = "Sample_Group", samGroup = gb$col_samGrp, # Point Colors
  betas = betas, targets = targets1, samShapes = samShapesCol, 
  samNames = gb$col_samNames, tsne_titles = gb$tsne_titles[1:3]
)
invisible(gc(verbose = F))
```

# All Groups Unsupervised TSNE (No Shapes) 

## `r I(as.character(gb$tsneHead2))` {.tabset}
```{r, label='TSNE Unsupervised2', echo=FALSE, error=FALSE, fig.keep='all', message=FALSE, warning=FALSE, cache=FALSE, dpi=300, out.height="650px", out.width="3600px", results='asis', fig.path="figures/tsne/"}
targets <- gb$colorTargets(targets, gb$col_shapes)
targets1 <- gb$SubsetTargets(targets)
samShapesCol = "Sample_Group" #samShapes = targets1[, gb$col_samGrp]
gb$subsetBetas(
  targFilter = "Sample_Group", samGroup = gb$col_samGrp, # Point Colors
  betas = betas, targets = targets1, samShapes = samShapesCol,
  samNames = gb$col_samNames, tsne_titles = gb$tsne_titles[1:3]
)
invisible(gc(verbose = F))
```

## All groups Supervised TSNE {.tabset}
```{r, label='TSNE Supervised1', results='asis', fig.keep='all', out.width="1200px", out.height="1000px", dpi=300, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, error=TRUE, fig.path = "figures/tsne/"}
targets1 <- gb$SubsetTargets(targets)
targets1$Sym_Shape <- gb$sam.grp.type
samShapes = targets1[, gb$col_samTypes]
if (gb$supervisedRun == T) {
    gb$subsetBetas(targFilter = "Sample_Group", samGroup = gb$col_samGrp, # Point Colors
                   betas = betas, targets = targets1, samShapes = samShapes,
                   samNames = gb$col_samNames, tsne_titles = gb$tsne_titles[4:6], supervised = T
                   )
    invisible(gc(verbose = F))
} else{cat("No supervised analysis output")}
```
<p><hr class="solid"> </hr></p>
# HeatMaps
```{r, label='HM-unsupervised-annotations', include=FALSE, echo=FALSE, class.source="bg-success", results='asis', fig.keep='all', message=FALSE, fig.path = "figures/heatmaps/"}
gb$LoadHeatMapLibs()
targets1 <- gb$SubsetTargets(targets)
betas1 <- betas[ , targets1[,gb$col_samNames]]
unBetas <- gb$tierBetas(betas1, gb$col_sentrix, RGSet) #unsupervised betas
unBetas <- gb$addGeneName(RGSet, unBetas, gb$addGenesHm)
ha <- gb$AnnotateHmVars(targets1, gb$selectedVars)
ha <- gb$FilterHmAnno(ha, gb$selectedVars) # drop any unwanted columns
```

## All groups HeatMap (Unsupervised) {.tabset}
```{r, label='Unsupervised-HM-plot', fig.width=18, fig.height=22, dpi=300, echo=FALSE, fig.keep='all', results='asis', class.source = "bg-success", fig.path = "figures/heatmaps/"}
hm.db <- gb$LoopPrintHeatMap(unBetas, ha, geneNams=gb$addGenesHm, colSplt=3)
gb$LoopSaveHm(hm.db, gb$varProbes)
```

# Custom HeatMaps

```{r, label='HM-plot-custom-data', fig.width=18, fig.height=22, dpi=300, echo=FALSE, fig.keep='all', results='asis', class.source = "bg-success", fig.path = "figures/heatmaps/"}
probeList <- as.data.frame(readxl::read_excel("somefilename.xlsx", sheet = 3, skip = 6))[,"probe"]

rawBetas <- Get_Unfiltered_Betas(gb$idatPath, gb$samsheet)

toKeep <- probeList %in% rownames(rawBetas)
finalList <- probeList[toKeep]
probeBetas <- rawBetas[finalList,]

gb$PrintTableLists(
    ta1 = data.frame(`Probe List Used` = probeList),
    ta2 = data.frame(`Probes Missing` = probeList[!toKeep])
)
```

## Probe-Specific Heatmap (Unsupervised) {.tabset}

```{r, label='Unsupervised-HM-plot-custom', fig.width=18, fig.height=22, dpi=300, echo=FALSE, fig.keep='all', results='asis', class.source = "bg-success", fig.path = "figures/heatmaps/"}
gb$PrintSingleHeatMap(probeBetas, ha, geneNams=T, colSplt=3)
if(gb$generateCNVchunk==F){knitr::knit_exit()}
```

# Copy Number Plots
<p><hr class="solid"> </hr></p>
```{r, label='segfile-generation', fig.height=8, fig.width=15, fig.asp=0.75, include=FALSE, echo=FALSE, message=FALSE, fig.path = "figures/cnv/"}
gb$writeSegTab(gb$segFile, targets, idatPath=file.path(getwd(), "idats"))
cnData <- gb$grabClusterDat(gb$seg_clust_file, gb$segFile)
```
## CNV Frequency {.tabset}
```{r, label='CNV-plots', dpi=300, out.width='100%', fig.height=10, fig.width=16, echo=FALSE, warning=FALSE, class.source="bg-success", cache=FALSE, fig.show='asis', results='asis', error=FALSE, fig.keep='all', include=TRUE, message=FALSE, fig.path = "figures/cnv/"}
gb$SaveLoadCnvs(cnData[,1:(ncol(cnData))], plotName = "All", "All")
gb$GenCNVdataGroupSave(cnData, targets, gb$col_samGroup)
if(gb$genPathwaychunk == F){knitr::knit_exit()}
```
# Pathway Analysis
<p><hr class="solid"> </hr></p>
## Cluster Profiler {.tabset}
Cluster Condition: Tumor Type is `r toString(GroupSubset)` (`r toString(GroupSubset)`` vs All)
```{r, label='cluster profile', include=FALSE, echo=FALSE, fig.path = "figures/cluster/"}
geneVals <-gb$GetKeggGeneVals(RGSet, targets, nameGrp="SampleType", gb)
```
<p>**Displaying pathways with qvalue < 0.05** </p><br>
```{r, label='cluster gene', fig.height=10, fig.width=10, fig.asp=0.65, echo=FALSE, fig.path = "figures/pathway/" }
DT::datatable(geneVals[,1:7])
cat("\n\n")
topPaths <- geneVals[order(geneVals$pvalue),]
pathWayGenes <- gb$WritePathVals(geneVals, gb$geneListIn)
gb$LoopPathwayHeatMap(pathWayGenes, ha)
```
<p>**Pathways with lowest pvalue and lowest qvalue < 0.05** </p><br>
## Top 5 Pathways Genes List {.tabset}
```{r, label='Top pathways gene', echo=FALSE, include=TRUE, results='asis', fig.keep='all', fig.path = "figures/pathway/"}
gb$PrintPathways(pathWayGenes)
```
