---
output: html_document
classoption: landscape
editor_options: 
  chunk_output_type: console
params:
  runID: NULL
  sheetNamePath: NULL
  baseDir: NULL
  author: "Jonathan Serrano"
---
```{r,include=FALSE, cache=FALSE, cache.path="cache/",echo=FALSE}
# Check if RunID provided else use basename of working directory
if(is.null(params$runID)){
    runID = paste0(basename(getwd()))
}else{runID=params$runID}

message(paste("Using", runID, "as RunID"))

# Check if baseDir provided else use Desktop
if(is.null(params$baseDir)){
    baseDir = file.path("~","Desktop",runID)
}else{baseDir=params$baseDir}

message("Using the following base Directory:\n",baseDir)

# Check if sheetNamePath provided else use Desktop to look for samplesheet pattern
if(is.null(params$sheetNamePath)){
    sheetNamePath = list.files(baseDir,pattern = "_samplesheet.csv", full.names = T)[1]
}else{sheetNamePath = params$sheetNamePath}

message(paste0("Sample sheet name is: ", sheetNamePath))
fixerrors <- read.csv(sheetNamePath, strip.white = T)
targets <- minfi::read.metharray.sheet(baseDir, pattern = sheetNamePath)

if(nrow(fixerrors)<8){
    warning("Less than 8 samples are run, disabling biocparrallel")
    totNum<-1
}else{
# Check here if you have odd number of arrays used in makeLabels function
totNum <- nrow(fixerrors)/8 # total number of arrays for biocParrallel workers
}
targets$basenames <- fixerrors$Basename # path/to/idat/files
runID <- paste0(targets$RunID[1])
wsDate <- fixerrors$Date[1] #format(Sys.time(), '%d %B, %Y')
location <- file.path(baseDir,paste0( runID,"_Redcap.csv")) # redcap brain classifier file

if (!file.exists(location)) {
	warning(paste0("File not found: ", location,
	               "\nQC Summary Table will not generate"))
}

titleName <- paste("Methylation Sample QC for Batch", runID) #heading 1
fileName <- paste0(runID,"_QC.html") # output file name
pSubTitle <- 'Clinical Methylation Run' # subtitle
summarName <- paste("Classifier Report Summary for", runID) # summary table heading
```

---
title: "`r titleName`"
subtitle: "`r pSubTitle`"
author: "`r paste0(params$author)`"
date: "`r paste0(wsDate)`"
output:
  html_notebook:
    highlight: espresso
    theme: sandstone
    fig_caption: yes
classoption: landscape
always_allow_html: yes
papersize: a5
linestretch: 1.5
fontsize: 14pt
geometry:
- top=2mm
- left=2mm
- right=2mm
- bottom=2mm
editor_options:
  chunk_output_type: console
---

```{r set-options, include=FALSE, cache=FALSE, cache.path="cache/", echo=FALSE}
pkgs <- 
    c("knitr", "kableExtra", "magick", "webshot", "plyr", "ggplot2", "reshape2", "data.table", "DT", "plotly", "MethylAid", "minfi", "scales", "IlluminaHumanMethylation450kmanifest", "IlluminaHumanMethylationEPICmanifest", "IlluminaHumanMethylationEPICanno.ilm10b4.hg19", "Biobase", "RColorBrewer", "limma", "ggfortify", "Rtsne", "qdapTools", "gplots", "readxl", "stringr", "ggrepel", "Polychrome", "tinytex", "gridExtra", "rmarkdown", "BiocParallel", "pals", "grid", "grDevices")
if(!require("librarian")){install.packages("librarian", dependencies=T, verbose=T, Ncpus = 4, quiet=T)}
librarian::shelf(pkgs, ask=F)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(global.par = TRUE)
knitr::opts_knit$set(ask = F)
grDevices::devAskNewPage(ask = F)
R.utils::setOption("device.ask.default", FALSE)
```

```{r, label = "Margin Params", include=FALSE}
par(mar = c(8, 8, 0, 0)) #it's important to have that in a separate chunk
``` 

<style type="text/css">
h1.title{color: white; background-image: linear-gradient(to right, indigo, indigo, indigo, white, white); border-radius:18px; padding:5px; border-padding:6px;}
h2.section.level2{color: white; background-image: linear-gradient(to right, indigo, indigo, indigo, white, white); border-radius:18px; padding:5px; border-padding:6px;}

.main-container{max-width: 95% !important;margin-left:25px; padding: 10px;}
div.main-container{max-width: 95% !important;margin-left:25px; padding: 10px;}
div.container-fluid{max-width: 95% !important;margin-left:25px; padding: 10px;}
table.table.table-striped{margin-left:0px;margin-right:auto;align:"left";}
table{align:"left" !important;}
</style>

```{r SampleSheetfix, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(ggplot2)
## Get MU Data & Colors --------------------------------------
sheetNamePath <- list.files(baseDir,pattern = "_samplesheet.csv", full.names = T)[1]
message(paste0("Sample sheet name is: ", sheetNamePath))
fixerrors <- read.csv(sheetNamePath)
fixerrors$Basename <- file.path(getwd(),fixerrors$SentrixID_Pos)
```

```{r BioCParallel, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
mcc = parallel::detectCores()/2
BiocParallel::register(BiocParallel::MulticoreParam(mcc))
mcParam <- BiocParallel::MulticoreParam(workers = mcc, progressbar = T)

# MethylAid Summarize
sdata <- suppressWarnings(
    MethylAid::summarize(fixerrors, verbose=T, batchSize=round(totNum), force=TRUE, BPPARAM = mcParam))

qcProbes = list(BSI = "^BISULFITE CONVERSION I$", 
                BSII = "^BISULFITE CONVERSION II$",
                EC = "^EXTENSION$", SPI = "^SPECIFICITY I$", 
                HYB = "^HYBRIDIZATION$", 
                NP = "^NON-POLYMORPHIC$", 
                SPII = "^SPECIFICITY II$", 
                TR = "^TARGET REMOVAL$", 
                SC = "^STAINING$", NC = "^NEGATIVE$")

## MU --------------------------------------
rotateData <- function(data, columns){
	data[,columns] <- c(0.5*(data[,columns[1]] + data[,columns[2]]),
	                    data[,columns[1]] - data[,columns[2]])
	return(data)
}
## Subset Custom Data --------------------------------------
getNewData <- function(data_final, cutoff){
  dataList <- list(final_data = data_final)
  names(dataList) <- c("final_data")
  return(dataList)
}
## Get MU Data & Colors --------------------------------------
MU <- log2(t(sdata@MU)); targets <- sdata@targets; d <- sdata@plotdata
data_rotated <- rotateData(
    merge(MU, targets, by = "row.names"),
    columns = c("Methylated", "Unmethylated")
    )
data_rotated$x = data_rotated[,2]; data_rotated$y = data_rotated[,3]
MUvals <- getNewData(data_final = data_rotated, cutoff = 9)
```

```{r Plot parameters, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# function to increase vertical spacing between legend keys
draw_key_polygon3 <- function(data, params, size){
  lwd <- min(data$size, min(size) / 4)
  grid::rectGrob(
      width = grid::unit(1.5, "npc"), height = grid::unit(1.5, "npc"), 
      gp = grid::gpar(col = data$colour, fill = scales::alpha(data$fill, data$alpha), 
                      lty = data$linetype, lwd = lwd * .pt, linejoin = "mitre"))
}
# register new key drawing fun, global & persistent during R session
GeomBar$draw_key = draw_key_polygon3
set.seed(123)
plot.colours <- glasbey()[1:(length(MUvals$final_data$Sample_Name))]

## Generate Plot labels  ------------------
makeLabels <- function(totNum, xName, yName, plotName, thePlot) {
    legendLabel <- thePlot + xlab(xName) + ylab(yName) + ggtitle(plotName)  + 
        theme(
            plot.background = element_blank(),
            legend.title = element_text(size = 12),
            legend.text = element_text(size = 10),
            legend.key = element_rect(size = 2),
            axis.title = element_text(size = 14),
            legend.direction = "horizontal", 
            legend.position = "bottom",
            #text = element_text(size = 14),
            axis.text.x = element_text(size = 14),
            axis.text.y = element_text(size = 14),
            plot.margin = grid::unit(c(1, 1, 1, 1), 'cm'),
            legend.spacing.x = unit(0.20, 'cm'),
            legend.spacing.y = unit(0.65, 'cm'),
            legend.spacing = unit(0.20, 'cm'),
            plot.title = element_text(color = "navy", size = 26, face = "bold"),
            plot.subtitle = element_text(color = "black", size = 12),
            plot.caption = element_text(color = "darkgreen",face = "italic",size = 12)
            ) +
        labs(label = "", color = "") +
        guides(
            colour = guide_legend(
                title = "Samples",
                override.aes = list(fill = NA, shape = 19),
                byrow = TRUE,
                ncol = 9
            )) +
        coord_cartesian(clip = 'off') 
    return(legendLabel)
}
## Generate Plots for Probes --------------------------------------
plotParams <- function(totNum, dParam, xincept, yincept) {
    dParam = dParam$final_data
    dParam$Sample_Name = paste(dParam$Sample_Name, dParam$MP_num, sep = "\n")
    plot.colours <- glasbey()[1:(length(dParam$x))]
    
    thePlot <-
        ggplot(dParam,
            aes(
                x = dParam[, 2],
                y = dParam[, 3],
                color = dParam$Sample_Name,
                label = dParam$Sample_Name
                ), show.legend = F) +
        scale_color_manual(values = plot.colours) + geom_point(shape = 19,
                                                               size = 5,
                                                               alpha = 0.8) + 
        guides(color = guide_legend(nrow = totNum)) + theme_bw() +
        guides(color = guide_legend(ncol = 8)) + 
        scale_fill_manual(values = plot.colours) 
  
  if (yincept == 0){
      thePlot <- thePlot + ggrepel::geom_label_repel(
          aes(
              label = dParam$Sample_Name,
              size = 3,
              fill = dParam$Sample_Name,
              colour = alpha(c("black"), 1.0)
          ),
          fontface = 'bold',
          colour = alpha(c("black"), 1.0), alpha = 0.50,
          show.legend = F, segment.alpha = 0.30, segment.size = 0.75,
          direction = "both", max.overlaps = Inf, min.segment.length = 0.015,
          color = "black", label.size = 0.4, size = 3,
          nudge_x = ifelse(thePlot$data$x>mean(thePlot$data$x), -0.15, 0),
          nudge_y = ifelse(thePlot$data$y > mean(thePlot$data$y), -0.05, 0),
          point.padding = unit(0.25, "lines"), label.r = unit(0.5, "lines"), force = 12, max.iter = 10000) +
          geom_vline(xintercept = xincept, linetype = 'dashed', colour = "red") +
          coord_cartesian(clip="off") +
          expand_limits(x=min(dParam[,2]),y=max(dParam[,3])*0.25) +
          guides(fill = guide_legend(show.legend = F)) + theme(legend.position = "none") + 
          scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
          scale_y_continuous(breaks = scales::pretty_breaks(n = 10))
    }
  if (yincept != 0) {
      samlab <- c(str_replace(dParam$Sample_Name, c("\n"), "_"))
      thePlot <- thePlot + 
          geom_hline(yintercept = yincept, linetype = 'dashed', colour = "red") +
          annotate("text",x = dParam[, 2],y = (dParam[, 3]) - 0.007, 
                   label = samlab, angle = 90, size = 3) + 
          scale_x_continuous(breaks = scales::pretty_breaks()) + 
          guides(fill = guide_legend(show.legend = F)) + 
          theme(legend.position = "none")
      }
  return(thePlot)
}

```

```{r data Functions, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE, paged.print=FALSE}
## Get Plot Specific Probes --------------------------------------
getProbes <- function(probeName){d <- sdata@plotdata; d <- d[grepl(qcProbes[probeName], d$Type), ]
return(d)
}

## Merges Dataframe Values --------------------------------------
mergeDF <- function(df, tg) {
	mdf <- merge(df,tg,by = "row.names",suffixes = c("", ".y"))
	return(mdf)
}

## Get Data Values for Plot --------------------------------------
getData <- function(theD, exGrn, exRed, cutoff){
	dGrn <- theD[(exGrn), c(1:5, 7)]
	x <- tapply((dGrn$IntGrn), dGrn$Samples, mean)
	is.na(x) <- !is.finite(x)
	dRed <- theD[as.array(exRed), c(1:6)]
	df <- data.frame(x, y = tapply(dRed$IntRed, dRed$Samples, mean))
	mdf <- mergeDF(df,tg=targets)
	plot_data <- rotateData(mdf,columns = c("x", "y"))
	fdt <- plot_data; ott <- subset(plot_data, plot_data$x <= cutoff)
	return(list(final_data = fdt,outlier = ott))
}

get.hc.dat <- function() {
	d <- getProbes("HYB")
	d <- d[order(d$Samples),]
	hiD <- grepl("High", d$ExtendedType)
	loD <- grepl("Low", d$ExtendedType)
	x <- 0.5 * (d$IntGrn[hiD] + d$IntGrn[loD])
	y <- d$IntGrn[hiD] - d$IntGrn[loD]
	df <- data.frame(x = x, y = y, row.names = d$Samples[hiD])
	mdf <- mergeDF(df,tg = targets)
	return(mdf)
}

get.bs.dat <- function() {
	bsD = getProbes(probeName = "BSI")
	BSvals <- getData(theD = bsD, exGrn = grepl("C1|C2|C3", bsD$ExtendedType),
	                  exRed = grepl("C4|C5|C6", bsD$ExtendedType), cutoff = 10)
	return(BSvals)
}

get.op.dat <- function() {
	newD <- getProbes(probeName = "NP")
	OPvals <- getData(theD = newD, exGrn = newD$ExtendedType %in% c("NP (C)", "NP (G)"), 
					  exRed = newD$ExtendedType %in% c("NP (A)", "NP (T)"), cutoff = 11)
	return(OPvals)
}

swm <- function(funObj){return(suppressMessages(suppressWarnings(funObj)))}
```
\newpage
```{r Plot Getter, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE, paged.print=FALSE}

## Plot Names --------------------------------------

pltNames <- c(
    "Signal Intensity QC - Checks Raw signal quality (*MU > 9* is Passing)",
    "Biological Positive Control QC - Checks overall Amplification Performance (*SBPC > 11* is Passing)",
    "Bisulfite Conversion Control - Checks Zymo Kit Performance (*BS > 10* is Passing)",
    "Hybridization Control QC - Checks Probe Binding (*SHC > 12.75* is Passing)",
    "Negative Control QC - Checks negative probes above background (*Pvalue > 0.95* is Passing)"
    )

## MU Plot --------------------------------------
dat.mu <- swm(getNewData(data_rotated, cutoff = 9))
plotMU <- swm(plotParams(totNum, dParam = dat.mu, xincept = 9, yincept = 0))
plotMU <- swm(makeLabels(totNum, plotName = paste0(pltNames[1]), xName = "Log2 sqrt(M*U)", yName = "Log2 (M/U)", thePlot = plotMU))

## Plot OP Sample Dependent QC ------------------------------------
dat.op <- get.op.dat()
plotOP <- swm(plotParams(totNum, dParam = dat.op, xincept = 11, yincept = 0))
plotOP <- swm(makeLabels(totNum, plotName = paste0(pltNames[2]), xName = "log2 sqrt(R*G)", yName = "log2 (R/G)", thePlot = plotOP))

## Plot BS Biological Control --------------------------------------
dat.bs <- get.bs.dat()
plotBS <- swm(plotParams(totNum, dParam = dat.bs,xincept = 10,yincept = 0))
plotBS <- swm(makeLabels(totNum, plotName = paste0(pltNames[3]),xName = "log2 sqrt(R*G)", yName = "log2 (R/G)", thePlot = plotBS))

##Plot HC Hybridization Control--------------------------------------
dat.hc <- get.hc.dat()
plotHC <- swm(plotParams(totNum, dParam = getNewData(dat.hc, cutoff = 12.75),xincept = 12.75, yincept = 0))
plotHC <- swm(makeLabels(totNum, plotName = paste0(pltNames[4]),xName = "log2 sqrt(H*L)", yName = "log2 (H/L)", thePlot = plotHC))

## Plot DP --------------------------------------
df <- data.frame(x=1:length(sdata@DPfreq), y=sdata@DPfreq, row.names=names(sdata@DPfreq)); dat.dp <- mergeDF(df, tg=targets)
plotDP <- swm(plotParams(totNum, dParam = getNewData(dat.dp, cutoff = 0.95), xincept = 0, yincept = 0.95))
plotDP <- swm(makeLabels(totNum, plotName = paste0(pltNames[5]), xName = "Samples", yName = "Pvalue", thePlot = plotDP))
```
\newpage

```{r MU_plot1, echo=FALSE, error=FALSE, fig.align="center",  fig.margin=TRUE,  message=FALSE, warning=FALSE, fig.width=18.5, fig.height=12, include=FALSE}
pltCap <- paste(targets$RunID[1])
pmu <- plotMU + ggplot2::labs(
    subtitle = "Median methylated vs unmethylated log2 intensity plot checks for the raw signal quality per sample. For each CpG site,\nmethylated and unmethylated measurements are produced. The measure of relative methylation levels depend on these signal intensities.\nSamples falling **above threshold (MU > 9) pass QC** and anything below the threshold are considered QC Failed samples.\n", caption = pltCap)
failedMU <- plotMU$data$x <= 9
failedMU <- plotMU$data$MP_num[failedMU]
```

<style>hr.solid {border-top: 3px solid #bbb;}</style>

\newpage
```{r MU_plot2, echo=FALSE, error=FALSE, fig.align="center", fig.margin=TRUE,  message=FALSE, warning=FALSE, fig.width=18.5, fig.height=12, include=FALSE}
plotMU2 <- pmu 
```
<hr class="solid">
\newpage
```{r OP_plot, echo=FALSE, error=FALSE, fig.align="center", fig.margin=TRUE,  message=FALSE, warning=FALSE, fig.width=18.5, fig.height=12}
plotMU2 + ggplot2::theme(plot.title = ggplot2::element_text(color = "navy", size = 26, face = "bold"))
plotOP + ggplot2::labs(subtitle ="Sample biological positive control is assessed based on Non-polymorphic (NP) control probes. NP controls are used to test the overall performance of assay from amplification to detection.\nSamples falling **above threshold (SBPC > 11) pass** this QC and anything below the threshold are considered bad samples.\n", caption = pltCap)
failedOP <- plotOP$data$x <= 11; failedOP <- plotOP$data$MP_num[failedOP]
```
<hr class="solid">
\newpage
```{r BS_Plot, echo=FALSE, warning=FALSE, fig.align="center", message=FALSE, fig.margin = TRUE,fig.width=18.5, fig.height=12}
plotBS + ggplot2::labs(subtitle = "Bisulfite conversion quality is assessed based on Bisulfite Conversion I (BSI) control probes. BSI control probes use Infinium I probe design to monitor efficiency of bisulfite conversion.\nSamples falling **above threshold (BS > 10) pass** this QC and anything below the threshold are considered bad samples.\n", caption = pltCap)
failedBS <- plotBS$data$x <= 10
failedBS <- plotBS$data$MP_num[failedBS]
```
<hr class="solid">
\newpage
```{r HC_Plot, echo=FALSE,  fig.margin=TRUE,  warning=FALSE, fig.align="center", message=FALSE, fig.width=18.5, fig.height=12}
plotHC + ggplot2::labs(subtitle = "Sample hybridization is assessed based on Hybridization control (HC) probes.\nHC probes test the overall performance of the entire assay using synthetic targets instead of amplified DNA.\n**Samples falling above threshold (SHC > 12.75) pass this QC** and anything below the threshold are considered QC Failed samples.",
caption = pltCap)

failedHC <- plotHC$data$x <= 12.75
failedHC <- plotHC$data$MP_num[failedHC]
```
<hr class="solid">
\newpage
```{r DP_Plot, fig.margin=TRUE,  echo=FALSE, warning=FALSE, fig.align="center", message=FALSE, fig.width=18, fig.height=12}

plotDP + ggplot2::labs(subtitle = "Sample negative control is assessed based on negative control (NC) probes. NC are randomly permuted sequences that should not hybridize to DNA template.\nThe mean signal of these probes defines the background of the system.\nTo be considered as passing this QC, **less than 95%** of probes should be above the background signal.", 
                       caption = pltCap)
failedDP <- plotDP$data$y <= 0.95
failedDP <- plotDP$data$MP_num[failedDP]
```
\newpage
```{r checkQC, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
summaryFail <- runName <- NULL
runName <- paste(targets$RunID[1])
if (is.null(runName)) {runName = paste0(basename(getwd()))}
location <- file.path("~","Desktop","runName",paste0(runName,"_Redcap.csv"))
if(!file.exists(location)){knitr::knit_exit()}
```
<hr class="solid"><div style="background-image: linear-gradient(to right, mediumpurple,mediumpurple,mediumpurple, white, white); border-radius: 18px; padding: 5px; border-padding:6px;"><h2 style="color: White;">
```{r, summartitle, echo=FALSE, results='asis', out.width="50%"}
cat(summarName)
```
</h2></div>
<div style="align:left;margin-right:auto;margin-left:0px;">
```{r Summary, fig.align="left", message=FALSE, echo=FALSE, warning=FALSE}
library("kableExtra")
library(dplyr)
clas.tb <- read.csv(location, strip.white = T)
#tabTitle <- paste0("<center><strong>",runName," Table Results Summary","</strong></center>")
genSumFail <- function(failPlot, failTex, sf=summaryFail){
	ftx = paste("<h4>The following samples **Failed", failTex, "QC:**</h4>")
	if (length(failPlot)>0){
		sf <- paste(sf,paste(ftx,paste0(failPlot,"</li>\n"),sep="\n<li>"))
		}
	return(sf)
}
summaryFail <- genSumFail(failedMU, "Signal intensity")
summaryFail <- genSumFail(failedOP, "Positive Control")
summaryFail <- genSumFail(failedBS, "Bisulfite Conversion")
summaryFail <- genSumFail(failedHC, "Probe Hybridization")
summaryFail <- genSumFail(failedDP, "Negative Control")
summaryFail <- paste(summaryFail, sep = "\n", collapse = "</li>\n")
newHeads <- c("RD-number", "B-Number", "TM-number", "Methylation Class",
			  "Classifier Score", "Subgroup", "Subscore", "MGMT Status")
gCol <- ifelse(clas.tb$mgmt_status == "methylated", "red", "blue")
gCel <- ifelse(clas.tb$classifier_value < 0.90, "red", "green")
bNum =  clas.tb$b_number
tableSum <- clas.tb %>% 
	dplyr::mutate(
		classifier_value = 
			cell_spec(classifier_value, "html", color = gCel, bold = T),mgmt_status = 
			cell_spec(mgmt_status, "html", color = gCol)) %>% 
	dplyr::select(record_id, b_number, tm_number, classifier_score, 
				  classifier_value, subgroup, subgroup_score, mgmt_status) %>%
	kable(format="html",booktabs=TRUE,linesep="",align="c",escape=FALSE,
		  col.names=newHeads)%>%
	kable_styling("striped",position="left") %>%
	row_spec(which(grepl('control',bNum)),bold=TRUE, color="white",background="orange")%>%
	row_spec(which(grepl('low',bNum)), bold=TRUE,color="white",background="salmon")%>%
	row_spec(which(grepl('_',bNum)),bold=TRUE, color="white",background="salmon")%>%
	kable_styling(latex_options="scale_down")

tableSum %>% kable_styling(position="left")

jb="<h4>The following samples did not classify with a score >0.90:</h4>\n\n"
failText <- paste("", jb, sep = "\n\n")
lowScoring <- paste(paste0("**",clas.tb$record_id[clas.tb$classifier_value < 0.90],"**"),
				    clas.tb$classifier_value[clas.tb$classifier_value < 0.90],sep = ", ")
scoreList <- c("\n")
failedSams <- lapply(lowScoring, FUN = function(x){scoreList <- paste(scoreList, x,"</li>\n")})
failedSams <- paste("<li>",failedSams, sep = "")
controlSample <- paste0(clas.tb$tm_number[(which(grepl('control',bNum)))])
controlSample <- paste(controlSample, sep = "\n")
```
</div>
\newpage
<p>
<h3 style="color:#3CB371">PC Control:
```{r, post_note_two, echo=FALSE, results='asis'}
if(!is.null(controlSample)) {cat(controlSample, sep = "\n\n")}
```
</h3></p>
<h4>Control Sample Comments</h4>
<p class="comment">No additional Bioinformatic Comments</p><br>
<div style="background-image: linear-gradient(to right, mediumpurple, white, white); border-radius: 18px; padding: 5px; border-padding:6px;">
<h2 style="color: White;"> QC Summary</h2>
</div>
<p class="comment" style="width: 40%;">
<style>
ul li {background: #ffe5e5;padding: 10px;margin: 5px;font-size:16px;list-style-type: none;width: 35%;}
</style>
<ul style="color:darkred; background: #ff9999; padding: 10px; margin-left: 35px;list-style-type: none;width: 35%;">
```{r, post_note, echo=FALSE, results='asis', out.width="50%"}
 if (!is.null(summaryFail) & summaryFail !="") {
 	cat(summaryFail, sep = "\n\n")
 	} else {cat("All samples **Passed each QC Critera**", sep = "\n\n")}
```
</ul>

<div style="background-image: linear-gradient(to right, mediumpurple, white, white); border-radius: 18px; padding: 5px; border-padding:6px;">
<h2 style="color: White;"> Classifier Scores Summary</h2>
</div>
<p></p>
<ul style= "color:black; background: lightblue; padding: 10px; margin-left: 35px;list-style-type: none;width: 35%;">
```{r, post_note2, echo=FALSE, results='asis', out.width="50%"}
if (length(failedSams)>0) {
	cat(failText,sep="\n\n");cat(failedSams,sep="");cat("", sep="\n\n")
	}else{cat("All samples classified with positive matches", sep = "\n\n")}
```
</ul>
</p> 
<p style="color:#00008B;font-size:16px;">
<b>Note:</b> 
Having a Brain Classifier Score below 0.90 does not indicate the sample failed QC.</p>
<p style="color:#00008B;font-size:16px;">Brain classifier output score is not included as part of sample QC. Samples can pass QC and also have no matching Brain tumor classification.
</p>

<p class="comment">
```{r Summary_notes, echo=FALSE, fig.align="center", fig.width=18, fig.height=12, message=FALSE, warning=FALSE}
library("knitr")
library("kableExtra")
library(dplyr)

worksheetNam <- paste0(getwd(),"/",runName,".xlsm")
columnCss <- "border-width:2px;border-style:solid;background-color:rgb(255,250,205);
border-color:rgb(105,105,105); width: 800px;"
rowCss <- "color:white; text-align: center;font-weight: bold; border-color:rgb(105,105,105);"
if (file.exists(worksheetNam) & file.exists(location)) {
  noteData <- as.data.frame(
  	readxl::read_excel(worksheetNam, sheet = 2,range = "M1:M7",col_types = c("text")))
rownames(noteData) <- NULL
noteData <- noteData[!is.na(noteData), ]
noteData <- as.data.frame(noteData)
noteData <- noteData[noteData!=0,1]
noteData <- as.data.frame(noteData)
colnames(noteData) <- "Worksheet Notes"
noteData %>% kable("html", booktabs = T, escape = F, linesep = "") %>%
    kable_styling("striped",full_width = F, font_size = 16, position = "left") %>%
    column_spec(column = c(1), extra_css = columnCss) %>%
    row_spec(row = 0, font_size = 24, background = "rgb(139,69,19)", extra_css = rowCss)
}
#beepr::beep("treasure")
```
