---
title: "Methylation Profiling Report (v11)"
author: "Quick Links:"
output: 
 html_document: 
   toc: yes
   toc_collapsed: no
   includes:
     in_header: logos.html
editor_options: 
  chunk_output_type: console
params:
    token: "NONE"
    rundata: NULL
---
<style type="text/css">
h1.title{color: white; background-image: linear-gradient(to right, indigo, indigo, indigo, white, white); border-radius:18px; padding:5px; border-padding:5px;}
</style>
```{r global_options, include=FALSE, warning=FALSE}
stopifnot(!is.null(params$rundata))

message("params$rundata")
print(params$rundata)

if(!require("librarian")){install.packages("librarian", dependencies=T, verbose=T, quiet=T)}
# Setting US CRAN REPO
rlis = getOption("repos")
rlis["CRAN"] = "http://cran.us.r-project.org"
try(options(repos = rlis), silent=T)
# List of all Packages
pkgs <- c(
    "needs",
    "knitr",
    "jsonlite",
    "crayon",
    "RCurl",
    "ggplot2",
    "kableExtra",
    "tidyverse",
    "plotly",
    "pkgdown",
    "ggplot2",
    "magrittr",
    "compiler",
    "minfi",
    "parallel",
    "progressr",
    "doParallel")

librarian::shelf(pkgs, ask=F,verbose=F, warn.conflicts = F, quietly = T)
#library(progressr)
#progressr::handlers("txtprogressbar")
#progressr::handlers(global = TRUE)

require("needs")
library("knitr")
optsLi <- list(error = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.align="left", self.contained=TRUE, comment='', tidy.opts=FALSE, label_list=FALSE, highlight=FALSE, error = TRUE)

knitr::opts_chunk$set(optsLi)
knitr::opts_knit$set(optsLi)
knitr::opts_current$set(optsLi)
knitr::opts_knit$set(quiet = FALSE)
knitr::opts_knit$set(progress = TRUE)
knitr::opts_knit$set(verbose = TRUE)
#knitr::opts_knit$set(progress_handler = progressr::handlers(progressr::handler_progress()))
```

```{r setup, cache.path="cache/", include=FALSE, cache=FALSE}
knitr::opts_chunk$set(error = TRUE, echo = FALSE, message = FALSE, warning = FALSE, self.contained=TRUE, comment = '', cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')))
options(scipen = 5)
require("compiler")
supM <- function(objTing){return(suppressMessages(suppressWarnings(objTing)))}
assign(x = "supM", value = supM, envir = .GlobalEnv)
supM(compiler::enableJIT(3))
supM(compiler::compilePKGS(enable = TRUE))
supM(compiler::setCompilerOptions(suppressAll = TRUE, optimize = 3))

if(getRversion() >= 4.0){ #Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) &&
    doParallel::registerDoParallel(parallel::detectCores() - 2)
    parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
} else{message("~~~~~~~~~~~~Not using R >= 4.0\n")}

# load ggplot2 silently
supM(library(verbose=F,warn.conflicts = F, quietly = T, package=ggplot2))


getScores <- function(Mset=NULL){
	if(!is.null(Mset)){
  betas <- minfi::getBeta(Mset)
  ex <- which(!names(mnp.v11b6::refset.center) %in% rownames(Mset))
  if (length(ex) > 0)
    refset.center <- mnp.v11b6::refset.center[-ex]
  betas <- betas[match(names(refset.center), rownames(betas)), ]
  betas <- betas - refset.center
  betas <- t(as.matrix(betas, ncol = 1))
  if (length(ex) > 0)
      pcaloadings <- mnp.v11b6::pcaloadings[-ex, ]
  sc <- betas %*% pcaloadings
  scores <- rbind(mnp.v11b6::pcascores, sc)
  return(na.exclude(scores))}
}

MNPtsne2 <- function(scores=NULL){
	if(!is.null(scores)){Rtsne::Rtsne(scores, dims = 3, pca = F, max_iter = 1500, theta = 0, perplexity = 30, num_threads = 1, is_distance = F)}
}
set.seed(seed = 12345)
getScore_cache = compiler::cmpfun(getScores)
tsne_cache = compiler::cmpfun(MNPtsne2)
#tsne_cache <- local(MNPtsne.cmpfun())
#bookdown::gitbook::html_document2()
```
<style>
body {font-family: Arial, Helvetica, sans-serif;padding: 10px}
hr.dashed {border-top: 3px dashed #bbb;}
hr.dotted {border-top: 3px dotted #bbb;}
hr.solid {border-top: 3px solid #bbb;}
hr.rounded {border-top: 8px solid #bbb; border-radius: 5px;}
div.main-container {max-width: 96% !important; margin-left: 20px;padding: 10px;}
htmlwidget-4f278c17b77c3d0e3cff {max-width: 50% !important; height: 200px !important;}
htmlwidget-8fc54d1bca00894e9b67 {max-width: 50% !important; height: 200px !important;}
</style>

<style type="text/css">
.main-container {max-width: 96% !important; margin-left:25px; padding: 10px;}
div.main-container{max-width: 96% !important;margin-left: 20px;padding: 10px;}
div.container-fluid{max-width: 96% !important; margin-left: 20px;padding: 10px;}
ul.no-bullets {list-style-type: none;}
</style>

<hr class="solid">
<h2 style="border: 4px solid burlywood; border-radius: 10px; padding: 10px;width:fit-content; width:-webkit-fit-content; width:-moz-fit-content;">
Sample Information 
</h2>
<div style="background-image: linear-gradient(180deg, BlanchedAlmond, white); font-size: 16px">

```{r 'Sample Info', class.source="bg-success", size="normalsize"}
	dat <- params$rundata
	sample = 1
run_id = paste(dat$run_id)
tech = paste(dat$tech)
tech2 = paste(dat$tech2)
bnumber = paste(dat$bnumber)
mp_number = paste(dat$mp_number)
sampleID = paste(dat$sampleID)
RGset = RGsetEpic
RGset <- RGset[,sample]
RGset2 <- RGset
FFPE=NULL

stopifnot(!is.null(run_id)|!is.null(tech)|!is.null(tech2)|!is.null(bnumber)|!is.null(RGset))

redfolder <- file.path("~","Desktop", run_id)
redFile <- paste0(run_id,"_Redcap.csv")
redcsv <- file.path(redfolder,redFile)

is450k <- RGset@annotation[[1]] == "IlluminaHumanMethylation450k"

redcapDF <- data.frame(
    record_id = character(),
    b_number = character(),
    barcode_and_row_column = character(),
    array_type = character(),
    classifier_sex = character(),
    classifier_score = character(),
    classifier_value = character(),
    subgroup = character(),
    subgroup_score = character(),
    mgmt_status = character(),
    mlh1_status = character(),
    mlh1_pos_loci = character(),
    second_tech = character(),
    primary_tech = character(),
    run_number = character(),
    tm_number = character()
)

if (!dir.exists(redfolder)) {dir.create(redfolder)}
if (!file.exists(redcsv)) {write.csv(x = redcapDF, file = redcsv, row.names = F)}
if (is450k) {
    easypackages::libraries("mnp.v11b4","IlluminaHumanMethylation450kmanifest")
	Mset <- mnp.v11b4::MNPpreprocessIllumina(RGset)
	if(is.null(FFPE)) FFPE <- mnp.v11b4::MNPgetFFPE(RGset)
	Mset_ba <- mnp.v11b4::MNPbatchadjust(Mset,FFPE)
	 if (FFPE=="Frozen"){
	     Mset@preprocessMethod <- c(Mset_ba@preprocessMethod, FFPE_Frozen.mnp.adjustment = '0.11')
	 }
	sex <- ifelse(mnp.v11b4::MNPgetSex(Mset)$predictedSex=="M","Male","Female")
	# Mset <- mnp.v11b4::MNPpreprocessIllumina(RGset)
	# Mset@annotation = c(array = "IlluminaHumanMethylation450k", annotation = "ilmn12.hg19")
	# if (is.null(FFPE)) {FFPE <- mnp.v11b4::MNPgetFFPE(RGset)}
	# Mset_ba <- mnp.v11b4::MNPbatchadjust(Mset, FFPE)
	# sex <- ifelse(mnp.v11b4::MNPgetSex(Mset)$predictedSex == "M", "male", "female")
	} else {
		Mset <- mnp.v11b6::MNPpreprocessIllumina(RGset)
		Mset@annotation=c(array="IlluminaHumanMethylationEPIC", annotation="ilm10b4.hg19")
		if (is.null(FFPE)) {FFPE <- mnp.v11b6::MNPgetFFPE(RGset)}
		Mset_ba <- mnp.v11b6::MNPbatchadjust(Mset, FFPE)
		detP <- minfi::detectionP(RGset)
		bs <- minfi::getBeta(Mset)
		sexEstimate <-as.data.frame(signif(sest::get.proportion_table(bs, detP), digits = 2))
		yest <- as.double(sexEstimate$`p.Y:(-18,-5]`) >= 0.75
		yest1 <- as.double(sexEstimate$`Y:(0,0.1]`) >= 0.12
		sex <- ifelse((yest == TRUE && yest1 == TRUE), "male", "female")
	}

sentrix <- colnames(RGset)
chiptype <- minfi::annotation(RGset)[[1]]
suppinfo <- c(sampleID,run_id,tech,bnumber,mp_number,sentrix,chiptype,FFPE,sex)
names(suppinfo) <- c("ID", "Batch ID", "Tech", "B-number", "MP-TN#", "Sentrix ID", "Array type", "Material type", "Gender")
suppinfo <- as.data.frame(suppinfo)
colnames(suppinfo) <- ""
supM(pander::pander(t(suppinfo), split.table = Inf))
```
</div>

<h3 style="color: Black;">

### Brain Tumor Methylation Classifier

</h3>
<h3><p></p></h3>

```{r 'Brain Classifier Family', size="normalsize"}
library(verbose=F, warn.conflicts = F, quietly = T, package= "knitr")
library(verbose=F, warn.conflicts = F, quietly = T, package= "kableExtra")
if (is450k==T) {
    library(verbose=F,warn.conflicts = F, quietly = T, package="mnp.v11b4")
    probs <- mnp.v11b4::MNPpredict(Mset_ba[, 1], type = 'prob')
	probs_mcf <- mnp.v11b4::MNPpredict(Mset_ba[, 1], type='prob',MCF=TRUE)
	} else {
	    library(verbose=F,warn.conflicts=F, quietly=T, package="mnp.v11b6")
	    tryCatch(
	        expr = {
	            probs <- mnp.v11b6::MNPpredict(Mset_ba[, 1], type = 'prob')
	            probs_mcf <- mnp.v11b6::MNPpredict(Mset_ba[, 1], type = 'prob', MCF = TRUE)
	        },
	        error = function(e) {
	            message("An error occured at Brain Classifier prediction:")
	            message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
	            message("Value of Mset_ba is:", "\n", paste0(Mset_ba[, 1]))
	            message("Trying MNPpredict_betas with Mset instead of Mset batch adjusted:\n")
	            probs <- mnp.v11b6::MNPpredict(Mset[, 1], type = 'prob')
	            probs_mcf <-
	                mnp.v11b6::MNPpredict(Mset[, 1], type = 'prob', MCF = TRUE)
	        }
	    )
}

oo <- order(probs, decreasing = T)
oo_mcf <- order(probs_mcf, decreasing = T)
eps <- 1e-3

out_class_family <- probs_mcf[oo_mcf[1:5]]
out_class_family <- cbind(round(pmax(pmin(out_class_family, 1 - eps), eps),3), colnames(probs_mcf)[oo_mcf][1:5])
out <- probs[oo[1:5]]
out <- cbind(round(pmax(pmin(out,1 - eps),eps),3),colnames(probs)[oo][1:5])

colnames(out_class_family) <- c("Class Score","Methylation Family")
colnames(out) <- c("Subgroup Score","Methylation Subgroup")

idx <- match(colnames(probs)[oo][1],mnp.v11b6::reflist[,2])
out_class_family <- as.data.frame(out_class_family)
out <- as.data.frame(out)
out_score <- as.numeric(paste0(out$`Subgroup Score`[1]))

subVal_int <- NULL
if (is.null(out_score)|is.na(out_score)) {
    warning("out_score value (sub score) is NULL.  Assigning value of 0.00")
    out_score <- 0.000
}
if (out_score >= 0.500) {subVal_int <- "Positive"}
if (out_score < 0.500 & out_score >= 0.100) {subVal_int <- "Indeterminate"}
if (out_score < 0.300) {subVal_int <- "Negative"}
if (is.null(subVal_int)) {
    warning("subscore value (subVal_int) is NULL")
    subVal_int <- "Indeterminate"
}

out$Interpretation = c(subVal_int,"","","","")
fsco <- as.numeric(paste0(out_class_family$`Class Score`[1]))

famVal <- NULL
if (is.null(fsco)|is.na(fsco)) {
    warning("fsco value (family score) is NULL.  Assigning value of 0.00")
    fsco <- 0.000
}
if (fsco >= 0.900) {famVal <- "Positive"}
if (fsco < 0.900 & fsco > 0.300) {famVal <- "Indeterminate"}
if (fsco <= 0.300) {famVal <- "Negative"}


if (is.null(famVal)) {
    warning("family value (famVal) is NULL")
    famVal <- "Indeterminate"
}
out_class_family$Interpretation = c(famVal,"","","","")
xtraCss1="border-radius:0px;border-width:1px;border-style:solid;border-color:rgb(192,192,192);"
xtraCss2="border-radius:0px;border-width:3px;border-style:solid;border-color:rgb(26,105,16);"
xtraCss3="border-radius:0px;border-width:3px;border-style:solid;border-color:rgb(16,28,105);"
txtc = "text-align:center;"
btso = c("bordered")
kgb <- c("striped",font_size = 14, bootstrap_options = btso)
kgh <- c(booktabs = T, escape = F, linesep = "")

out_class_family %>% 
	knitr::kable("html",kgh,align='clc') %>%
	kableExtra::kable_styling(kgb,full_width=F,position="float_left") %>%
	kableExtra::column_spec(column=c(1,2),extra_css=xtraCss1) %>%
	kableExtra::column_spec(column=2,background="rgb(204,255,204)",extra_css=txtc) %>%
	kableExtra::row_spec(row=0,font_size=16,background="rgb(127,217,126)",color="black") %>%
	kableExtra::row_spec(row=1,extra_css=xtraCss2)
			
out %>% 
	knitr::kable("html",kgh,align='clc')%>%
    kableExtra::kable_styling(kgb,full_width=F,position="left") %>%
	kableExtra::column_spec(column=c(1,2), extra_css=xtraCss1) %>%
	kableExtra::column_spec(column=2,background="rgb(204,230,255)", extra_css=txtc) %>%
	kableExtra::row_spec(row=0,font_size=16,background="rgb(135,174,237)", color="black") %>%
	kableExtra::row_spec(row=1,extra_css=xtraCss3)

familia <- out_class_family$`Methylation Family`[1]
fscore <- out_class_family$`Class Score`[1]
subfam <- out$`Methylation Subgroup`[1]
subScore <- out$`Subgroup Score`[1]

```
<caption style="font-size:12px;"><ul style="font-size:12px; list-style-type: none;" class="no-bullets">
<b style="font-size:13px;">Interpretation Key</b>

<li><strong>Positive</strong> 
indicates a positive match for methylation classifier (score >= 0.9) & Match to MC family member quality cases. 
(score >= 0.5)
</li>

<li><strong>Indeterminate</strong>
indicates no determinate match (score < 0.9): possibly still relevant for low tumor content and low DNA.  For subclass score, indeterminate value is <0.5 and >=0.1
</li>

<li><strong>Negative</strong>
indicates no matching methylation class (score <0.3) and for classifier subclass score is <0.1 
</li></ul></caption>

<h4> Methylation Class Description</h4>

<p style="font-size:14px; border-radius:10px; border-width:2px; border-style:solid; border-color:rgb(192,192,192); padding:15px;border-padding:10px">
`r I(as.character(mnp.v11b6::reflist[idx,7]))`
</p>
<hr class="solid">

<div>

<div style="background-image: linear-gradient(to right, mediumpurple, white, white);border-radius: 14px;padding: 4px; border-padding:5px;">
<h3 style="color: White;">

### TSNE Clustering

</h3>
</div>
```{r, label='TSNE Cluster', fig.height=8, fig.width=12}
me.col <- c( "#1F78B4","#2980BA","#3388C1","#3D91C8","#4799CF","hotpink","hotpink","hotpink","hotpink","hotpink","hotpink","#58D68D","#8FCDC0","#96D1B3","#9ED5A7","#A6D99B","#AEDD8F","#A9DB82","#97D574","#85CF65","#74C957","#62C349","#50BD3A","#3EB72C","#2DB11D","#26AC17","#41AA27","#5BA737","#76A547","#ff4d00","#ABA068","#ff4d00","#E09C88","#FA9998","#ff4d00","#F48D78","#ff4d00","#ED8157","#EA7B47","#E77536","#E46F26","#E06916","#E26F1A","#E67A25","#E98531","#ED8F3C","#F09A47","#F4A452","#F7AF5E","#FBB969","#FDB368","#FD9C5A","#FD854D","#FD6D3F","#FE5632","#FE3F24","#FE2817","#FE110A","#FC0406","#F11421","#E6253B","#DC3556","#D14670","#C6568B","#BC67A5","#B177C0","#A687DB","#A17DDB","#9C72DC","#9668DC","#915DDD","#8B53DE","#8648DE","#803EDF","#7B33DF","#863FCB","#9653B0","#A66795","#B67B7A","#C68F5F","#D6A343","#E6B728","#F6CB0D","#FFFF00","#FFFF00","#FFFF00","#F6D916","#5e2f1b","#2980B9","#b8b8b8","#A9A9A9","#A9A9A9","#A9A9A9","#A9A9A9","#9E9E9E","#939393","#868686","#787878","#676767","#0400ff" )
set.seed(12345)

res<-NULL
if(is450k==TRUE){
    res=mnp.v11b4::MNPtsne(Mset_ba)
    } else {
        scores <- getScore_cache(Mset_ba)
        res <- tsne_cache(scores)
        }
Tsne_1 <- res$Y[,1]; Tsne_2 <- res$Y[,2]
plTxt <- paste0("<b>",sampleID,"</b>")
t1 = Tsne_1[2802]; t2 = Tsne_2[2802]
# Arrow annotation for sample
a <- list(x = t1, y = t2, text = plTxt, xref = "x", yref = "y", size = 0.7, 
          bgcolor = 'rgba(255, 255, 255, 0.5)',
          font = list(size = 13, color = "dimgray"), showarrow = T, 
          arrowhead = 0, ax = 50, ay = -50, arrowsize = 1, arrowcolor = "orange")
# Line properties
lnd <- list(color = "red", alpha = 0.8, width = 0.75,dash = 'dash')
vline<-function(x=0){list(type="line",y0=0,y1=1,yref="paper",x0=x,x1=x,line=lnd)}
hline<-function(y=0){list(type="line",x0=0,x1=1,xref="paper",y0=y,y1=y,line=lnd)}
# Font parameters
f1 <- list(family = "Arial,sans-serif", size = 18, color = "darkgrey")
f2 <- list(size = 14, face = "bold")
d1 <- list(titlefont=f1, showticklabels=T, tickfont=f1, zerolinecolor=plotly::toRGB("grey"), zerolinewidth=0.5)
b1 <- c(list(title = "T-sne 1"), d1)
b2 <- c(list(title = "T-sne 2"), d1)
m1 <- list(size = 12, line = list(width = 1.7, color = 'DarkSlateGrey'))

theplot <- plotly::plot_ly(x = ~ Tsne_1, y = ~ Tsne_2, color = ~methclass, colors = me.col, opacity = 0.9, 
                           marker = list(size = 5), font = f2)
theplot <- theplot %>%
	plotly::layout(type = "scatter", shapes = list(vline(t1), hline(t2))) %>%
	plotly::layout(legend = list(orientation = "h", xanchor = "center")) %>%
	plotly::layout(xaxis = b1, yaxis = b2, showlegend = T) %>%
	plotly::layout(type = "scatter", annotations = a, size = 1.5)
theplot <- theplot %>% plotly::add_trace(theplot, mode = 'markers', type = "scatter", marker = m1)
theplot <- theplot %>% plotly::layout(legend = list(orientation = "v", xanchor = "right", x = 1.1))
supM(theplot)
```
<hr class="solid">
<div style="background-image: linear-gradient(to right, mediumpurple, white, white); border-radius: 14px; padding:4px; border-padding:5px;">
<h3 style="color: White;">
### Copy Number Variation Profile
</h3>
</div>
```{r, label='CNV Plot', fig.width = 12, fig.height=7}
if (is450k==TRUE) {
    library(verbose=F,warn.conflicts = F, quietly = T, package="mnp.v11b4")
    MNPcnv450k <- function(Mset, sex = NULL, ...){
        path <- file.path(path.package('mnp.v11b4'), 'ext')
        if (is.null(sex)) {
            Rset <- ratioConvert(Mset, what = "both", keepCN = TRUE)
            sex <- ifelse(MNPgetSex(Rset)$predictedSex == "M", "Male", "Female")
        }
        load(file.path(path, "CNanalysis4_conumee_ANNO.vh20150715.RData"))
        cndata <- conumee::CNV.load(Mset)
        if (sex == "Male") {
            load(file.path(path, "CNanalysis4_conumee_REF-M.vh20150715.RData"))
            x <- conumee::CNV.fit(cndata, refM.data, annoXY)
        }
        if (sex == "Female") {
            load(file.path(path, "CNanalysis4_conumee_REF-F.vh20150715.RData"))
            x <- conumee::CNV.fit(cndata, refF.data, annoXY)
        }
        x <- conumee::CNV.bin(x)
        x <- conumee::CNV.detail(x)
        x <- conumee::CNV.segment(x)
        return(x)
    }
    xx <- MNPcnv450k(Mset,sex = sex, main = sampleID)
	#mnp.v11b4::MNPcnvggplotly(xx)
    } else {
	    xx <- supM(mnp.v11b6::MNPcnv(Mset,sex = sex,main = sampleID))
	    }
supM(mnp.v11b6::MNPcnvggplotly(xx, getTables = F))
```
<p style= "font-size:14px">
Depiction of chromosomes 1 to 22 (and X/Y if automatic prediction was successful). Gains/amplifications represent positive, losses negative deviations from the baseline. 29 brain tumor relevant gene regions are highlighted for easier assessment.
</p>

### CNV Gains and Loss
```{r, label='CNV table'}
require(mnp.v11b6)
dra <- supM(mnp.v11b6::MNPcnvggplotly(xx,getTables = T))
gDF <- t(data.frame(Gains = c(rownames(dra[(dra$Gain == T),]))))
lDF <- t(data.frame(Loss = c(rownames(dra[(dra$Loss == T),]))))

extra_css1 = "border-radius:0px;border-width:1px;border-style:solid;border-color:rgb(192,192,192);"

tgDF <- 
	gDF %>% knitr::kable("html", kgh, align = 'clc') %>% 
	kableExtra::kable_styling(kgb,position = "left",full_width = F) %>%
	kableExtra::row_spec(row = 1, extra_css = extra_css1) %>% 
    kableExtra::column_spec(column = 1, background = "palegreen", extra_css = txtc)

tlDF <- 
	lDF %>% knitr::kable("html", kgh, align = 'clc') %>% 
	kableExtra::kable_styling(kgb,position = "left",full_width = F) %>%
	kableExtra::row_spec(row = 1, extra_css = extra_css1) %>% 
    kableExtra::column_spec(column = 1, background = "#CD5C5C", extra_css = txtc)

if (nrow(gDF) > 0) {tgDF}
if (nrow(lDF) > 0) {tlDF}
```

<p style= "font-size:12px">
(see Hovestadt & Zapatka, http://www.bioconductor.org/packages/devel/bioc/html/conumee.html)
</p>

<hr class="solid">
<div style=" background-image: linear-gradient(to right, mediumpurple, white, white);border-radius: 14px;padding: 4px;border-padding:5px;">
<h3 style="color: White;">
MGMT Prediction
</h3>
</div>

<div style="width:50%;">
```{r, include=FALSE, cache=TRUE}
require("tidyverse")
require("plotly")
require("ggplot2")
htmltools::tagList(plotly::ggplotly(ggplot2::ggplot(),width = 500, height = 200))
```
<div style="width:50%;height:200px">
```{r,label='MGMTPred', results='asis', out.width='50%', out.height='200px', plotly=TRUE, include=TRUE, fig.keep='all', fig.height=0.3, fig.width=1.5}
#
Mset_raw <- minfi::preprocessRaw(RGset) #, echo=FALSE, self.contained=TRUE

MNPciplot_mgmt<- function(Mset,sample=1){
    pred <- MNPpredict_mgmt(Mset[, sample])
    theBarPlot <- ggplot2::ggplot(pred, aes(x = Estimated, y = Status)) +
        geom_point(size = 5) +
        geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = .1, size = 1) +
        xlim(0, 1) +
        geom_vline(xintercept = pred$Cutoff, size = 1, colour = 'darkred') +
        theme(plot.title = element_text(lineheight = .8, face = "bold")) +
        xlab("Score") + ylab("") + scale_y_discrete("", breaks = c(0))
    return(plotly::ggplotly(theBarPlot))
}

if (is450k==T) {
    theBarPlot <- mnp.v11b4::MNPciplot_mgmt(Mset_raw)
    } else{theBarPlot <- supM(MNPciplot_mgmt(Mset_raw))}
#supM(thebarPlot)
#theBarPlot <- theBarPlot %>% layout(autosize = F, width = 500, height = 200)
theBarPlot <- htmltools::tagList(plotly::ggplotly(theBarPlot)) %>% layout(autosize = T, width = 500, height = 200)
supM(print(theBarPlot))
```
</div>
#### MGMT Status

```{r,label='MGMT tab', results='asis', fig.keep='all', out.width='50%', out.height='200px', plotly=TRUE, fig.height=1.5, fig.width=3.5, include=TRUE, self.contained=TRUE}
#
if (is450k) {
    mgmtData <- mnp.v11b4::MNPpredict_mgmt(Mset_raw)
} else{
    mgmtData <- mnp.v11b6::MNPpredict_mgmt(Mset_raw)
}
theTable <- supM(knitr::kable(mgmtData) %>% kableExtra::kable_styling(kgb,full_width = F, position = "left", font_size = 18))
theTable
```

<p style="font-size:9px">
see: Pierre Bady et al. *MGMT methylation analysis of glioblastoma on the Infinium methylation BeadChip identifies two distinct CpG regions associated with gene silencing and outcome, yielding a prediction model for comparisons across datasets, tumor
grades, and CIMP-status.* Acta Neuropathologica, p.547-560, Number 4, 2012.</p>
</div>

<hr class="solid">

<div style=" background-image: linear-gradient(to right, mediumpurple, white, white);border-radius: 14px; padding: 4px;border-padding:5px;">
<h3 style="color: White;">
### MLH1 Status Prediction 
</h3>
</div>
<div>
```{r, label='MLH1 Functions', fig.align="center", fig.height=12, fig.width=12, dpi=40}
get.clinical.data = function(ratioSet, RGset){
	#Output is DF with sample information, betas for relevant MLH1 loci
	MLH1_CGIDS = c("cg23658326","cg11600697","cg21490561","cg00893636")
	mlh.b = minfi::getBeta(ratioSet)[MLH1_CGIDS,]
	mlh.b <- as.data.frame(mlh.b)
	for (bal in 1:4) { if (is.nan(mlh.b[bal, 1])) {mlh.b[bal, 1] = 0.00}
		mlh.b[bal, 1] <- round(mlh.b[bal, 1], digits = 3)
		if (mlh.b[bal, 1] < 0.09) {mlh.b[bal, 1] = 0.00}
		if (mlh.b[bal, 1] > 1.00) {mlh.b[bal, 1] = 1.00} 
		else (mlh.b[bal, 1] = mlh.b[bal, 1])}
	#Calculate detection of Pvalues using minfi method #c(MGMT_CGIDS,MLH1_CGIDS),]
	detection.pvals = minfi::detectionP(RGset)
	l.pvals = detection.pvals[c(MLH1_CGIDS),]
	l.pvals <- as.data.frame(l.pvals)
	for (lpv in 1:4) {if (is.nan(l.pvals[lpv,1])) {l.pvals[lpv,1] = 0.00}
	    l.pvals[lpv,1] <- round(l.pvals[lpv,1], digits = 3)
		if (l.pvals[lpv,1] < 0.09){l.pvals[lpv,1] = 0.00}
		if (l.pvals[lpv,1] > 1.00){l.pvals[lpv,1] = 1.00} else {l.pvals[lpv,1] = l.pvals[lpv,1]}
		}
	#calculate number of methylated loci with beta values above cutoff for mlh1
	pos.loci = (mlh.b[1,] >= 0.18) + (mlh.b[2,] >= 0.27) + (mlh.b[3,] >= 0.13) + (mlh.b[4,] >= 0.09)
	m.reslt = rep("",length(pos.loci))
	m.reslt[pos.loci == 4] = "POSITIVE"
	m.reslt[pos.loci >= 0 & pos.loci < 3] = "NEGATIVE"
	m.reslt[pos.loci == 3] = "INDETERMINATE"
	
	all.data = data.frame(
	    Sample_Name = sample,
		cg23658326.MLH1 = mlh.b[1, ], cg11600697.MLH1 = mlh.b[2, ],
		cg21490561.MLH1 = mlh.b[3, ], cg00893636.MLH1 = mlh.b[4, ],
		MLH1.pos.loci = pos.loci, m.reslt = m.reslt,
		Pvalue.cg23658326 = l.pvals[1, ], Pvalue.cg11600697 = l.pvals[2, ],
		Pvalue.cg21490561 = l.pvals[3, ], Pvalue.cg00893636 = l.pvals[4, ], stringsAsFactors = F
		)
	return(all.data)
}

## Plot Beta densities for samples and plot ----------------------------------------------------------
getPlotTable = function(clin.data){
	title.string = c("MLH1 Result" = clin.data$m.reslt[1], "Total Positive Loci" = clin.data$MLH1.pos.loci[1])
	title.string <- as.data.frame(title.string); colnames(title.string) = NULL
	return(title.string)
}

## clean up beta.matrix values ------------
sanitizeDense <- function(beta.matrix){
	beta.matrix <- as.data.frame(beta.matrix)
	beta.matrix[is.na(beta.matrix)] <- 0
	beta.matrix[beta.matrix < 0] <- 0
	beta.matrix[beta.matrix > 1] <- 1
	beta.matrix <- round(beta.matrix, digits = 3)
	density <- density(beta.matrix[, 1])
	return(density)
}

## Print out the Plotly for Mlh1 ----------------------------------------------------------
renderPlot <- function(beta.matrix, clin.res) {
	clin.res <- clin.res[2:5]
	density <- sanitizeDense(beta.matrix)
	yTall = 1
	colNames <- c("cg23658326.MLH1", "cg11600697.MLH1", "cg21490561.MLH1", "cg00893636.MLH1")
	fl1 <- list(size = 16, face = "bold")
	fl2 <- list(family = "Arial, sans-serif", size = 20, color = "black")
	fig <- plotly::plot_ly(x = ~density$x, y = ~density$y, 
				   type = 'scatter', mode = 'lines', 
				   name = "Beta Values", font = fl1, showlegend = F) %>% 
		   plotly::layout(
		   	xaxis = list(title = 'Beta Values'), 
		   	yaxis = list(title = 'Density')
		   	)
	for (prd in colNames) {
		clr = clin.res[1, prd]
		txtL <- paste0(names(clin.res[prd]), round(clr, digits = 3))
		fig <- fig %>% plotly::add_segments(x = clr, y = 0, line = list(width = 15), yend = yTall, 
		                                    xend = clr, name = txtL, hoverinfo = txtL, showlegend = T)
		yTall <- yTall - 0.1
		}
	a <- list(titlefont = fl2, showticklabels = TRUE, tickfont = list(size = 16))
	lal <- list(orientation = "v", x = 0.08, y = 1)
	fig <- fig %>% plotly::layout(xaxis = a, yaxis = a, showlegend = T, legend = lal)
	return(suppressWarnings(fig))
	}

drawPlotTab <- function(mlhP){ 
	be = c(booktabs = T, escape = F, linesep = "")
	return(
		mlhP %>% knitr::kable("html",be, align = 'clc') %>% 
		    kableExtra::kable_styling(kgb,full_width = F, position="left") %>%
		    kableExtra::column_spec(column = 2, background = "rgb(204, 255, 204)", extra_css = txtc) %>% 
		    column_spec(column = 2, bold = T, border_right = T)
		)
	}

pipeline = function(RGset, getFig=F, getTable=F) {
	Mset = preprocessIllumina(RGset, bg.correct = TRUE, normalize = "controls")
	ratioSet = ratioConvert(Mset, what = "both", keepCN = FALSE)
	beta.matrix = getBeta(ratioSet)
	clin.res <- get.clinical.data(ratioSet, RGset)
	par(mar = c(5, 6, 4, 1) + .1)
	if (getFig == T) {theMlhplot <- renderPlot(beta.matrix, clin.res)
		return(theMlhplot)
	}
	if (getTable == T) {mlhP <- getPlotTable(clin.data = clin.res)
		return(mlhP)
	}
}
```

```{r, label='MLH1 Prediction', fig.align="center", fig.height=8, fig.width=10, dpi=36}
theMlhplot <- pipeline(RGset, getFig = T, getTable = F) 
supM(theMlhplot)
```
</div>

<div>
#### MLH1 Status

```{r, label='MLH1 plot'}
mlhP <- pipeline(RGset2,getFig = F, getTable = T)
theMlhTab <- drawPlotTab(mlhP)
theMlhTab
```

```{r, label='REDCapWrite', include=FALSE, message=TRUE, error=FALSE}
library("jsonlite")
library("crayon")
library("RCurl")
dfNewRed <- data.frame(
    record_id = sampleID,
    b_number = bnumber,
    barcode_and_row_column = sentrix,
    array_type = ifelse(is450k, yes = "450k", no = "EPIC"),
    classifier_sex = tolower(sex),
    classifier_score = familia,
    classifier_value = fscore,
    subgroup = subfam,
    subgroup_score = subScore,
    mgmt_status = mgmtData$Status,
    mlh1_status = mlhP[[1]][1],
    mlh1_pos_loci = mlhP[[1]][2],
    second_tech = tech2,
    primary_tech = tech,
    run_number = run_id,
    tm_number = mp_number
)

datarecord = jsonlite::toJSON((as.list(dfNewRed[1,])), auto_unbox=T)
message(datarecord)
message("~~",crayon::bgBlue("Record Uploaded:"))

makePost <- function(datarecord){
    ur = "https://redcap.nyumc.org/apps/redcap/api/"
    tk <- params$token
    RCurl::postForm(ur, token = tk, content = 'record', format = 'csv', type = 'flat',
                    data = datarecord, returnFormat = 'csv')
}

try(expr=makePost(datarecord),silent=T)

writeRedcap <- function(redcsv, dfNewRed,dfRedcap){
	redDF <- rbind(dfRedcap, dfNewRed)
	row.names(redDF) = NULL
	#write.table(dfNewRed, file= redcsv, row.names=F, col.names=T, append=T, quotes=F)
	write.csv(x = redDF,file = redcsv, row.names = F)
}
deskRunPath <- file.path("~", "Desktop", run_id)
redcsv <- list.files(path= deskRunPath, pattern="_Redcap.csv", full.names=T)[1]
if(!is.na(redcsv)){
dfRedcap = read.csv(redcsv, header = T, row.names = NULL)
dfRedcap <- as.data.frame(dfRedcap, row.names = NULL)
try(writeRedcap(redcsv, dfNewRed, dfRedcap), silent=T)
}else{
    message("REDCap Upload failed for sample:", sampleID, "will attempt upload at run end.")
}
```
</div>

<hr class="dotted">
#### Reference

#### [DNA methylation-based classification of central nervous system tumours](https://www.nature.com/articles/nature26000) 
<p style="font-size:9px">
David Capper, David T. W. Jones, Martin Sill, Volker Hovestadt, Daniel Schrimpf, Dominik Sturm, Christian Koelsche, Felix Sahm, Lukas Chavez, David E. Reuss, Annekathrin Kratz, Annika K. Wefers, Kristin Huang, Kristian W. Pajtler, Leonille Schweizer, Damian Stichel, Adriana Olar, Nils W. Engel, Kerstin Lindenberg, Patrick N. Harter, Anne K. Braczynski, Karl H. Plate, Hildegard Dohmen, Boyan K. Garvalov, Roland Coras, Annett Hölsken, Ekkehard Hewer, Melanie Bewerunge-Hudler, Matthias Schick, Roger Fischer, Rudi Beschorner, Jens Schittenhelm, Ori Staszewski, Khalida Wani, Pascale Varlet, Melanie Pages, Petra Temming, Dietmar Lohmann, Florian Selt, Hendrik Witt, Till Milde, Olaf Witt, Eleonora Aronica, Felice Giangaspero, Elisabeth Rushing, Wolfram Scheurlen, Christoph Geisenberger, Fausto J. Rodriguez, Albert Becker, Matthias Preusser, Christine Haberler, Rolf Bjerkvig, Jane Cryan, Michael Farrell, Martina Deckert, Jürgen Hench, Stephan Frank, Jonathan Serrano, Kasthuri Kannan, Aristotelis Tsirigos, Wolfgang Brück, Silvia Hofer, Stefanie Brehmer, Marcel Seiz-Rosenhagen, Daniel Hänggi, Volkmar Hans, Stephanie Rozsnoki, Jordan R. Hansford, Patricia Kohlhof, Bjarne W. Kristensen, Matt Lechner, Beatriz Lopes, Christian Mawrin, Ralf Ketter, Andreas Kulozik, Ziad Khatib, Frank Heppner, Arend Koch, Anne Jouvet, Catherine Keohane, Helmut Mühleisen, Wolf Mueller, Ute Pohl, Marco Prinz, Axel Benner, Marc Zapatka, Nicholas G. Gottardo, Pablo Hernáiz Driever, Christof M. Kramm, Hermann L. Müller, Stefan Rutkowski, Katja von Hoff, Michael C. Frühwald, Astrid Gnekow, Gudrun Fleischhack, Stephan Tippelt, Gabriele Calaminus, Camelia-Maria Monoranu, Arie Perry, Chris Jones, Thomas S. Jacques, Bernhard Radlwimmer, Marco Gessi, Torsten Pietsch, Johannes Schramm, Gabriele Schackert, Manfred Westphal, Guido Reifenberger, Pieter Wesseling, Michael Weller, Vincent Peter Collins, Ingmar Blümcke, Martin Bendszus, Jürgen Debus, Annie Huang, Nada Jabado, Paul A. Northcott, Werner Paulus, Amar Gajjar, Giles W. Robinson, Michael D. Taylor, Zane Jaunmuktane, Marina Ryzhova, Michael Platten, Andreas Unterberg, Wolfgang Wick, Matthias A. Karajannis, Michel Mittelbronn, Till Acker, Christian Hartmann, Kenneth Aldape, Ulrich Schüller, Rolf Buslei, Peter Lichter, Marcel Kool, Christel Herold-Mende, David W. Ellison, Martin Hasselblatt, Matija Snuderl, Sebastian Brandner, Andrey Korshunov, Andreas von Deimling & Stefan M. Pfister </p>

<span style="color:red"><p style="font-size:10px">
<b>Implementation of the results in a clinical setting is in the sole responsibility of the treating physician.</b>
</span>
</p>
