---
title: "Methylation Profiling Report"
author: "Quick Links:"
output: 
  html_document: 
    self_contained: yes
    mode: selfcontained
    keep_md: false
    toc: yes
    toc_collapsed: no
    clean: true
params:
    token: "NONE"
    rundata: NULL
    RGsetEpic: NULL
    knitDir: "NONE"
    envir : NULL
---

```{r set-options, echo=FALSE, cache=FALSE , message=FALSE, warning=FALSE}
gb <- globalenv(); assign("gb", gb)
dat <- params$rundata; assign("dat", params$rundata, envir=gb)
#saveRDS(params, file=file.path(fs::path_home(), "params.rds")) # Debug params <- readRDS("params.rds")
gitPath = "https://raw.githubusercontent.com/NYU-Molecular-Pathology/Methylation/main/R/Report-Scripts"
htmltools::includeCSS(file.path(gitPath,"SarcStyle.html"))
capture_env_hook <- function(before, options, envir) {if (before) {assign("chunk_env", environment(), envir = .GlobalEnv)}}
gb$RGset <- RGset <- params$RGsetEpic[, 1]
gb$msetDat <- gb$GetSexMsetBa(RGset, FFPE=NULL)
knitr::asis_output(gb$SuppInfoTable(dat, RGset, gb$msetDat))
```
### Brain Tumor Methylation Classifier Version 11
```{r 'Brain Classifier Family'}
gb$outList <- outList <- gb$supM(gb$GetOutClass(gb$msetDat))
classTables <- gb$GetClassProbTables(outList)
knitr::asis_output(classTables$famTable); knitr::asis_output(classTables$grpTable)
htmltools::includeHTML(file.path(gitPath,"InterpretKey.html"))
gb$theRefLi <- gb$GetRefList(gb$msetDat$Mset_ba, gb$outList)
```
<h4>Methylation Class Description</h4>
<p class="methtab">`r I(gb$theRefLi)`</p><hr class="solid">
###  Brain Tumor Methylation Classifier Version 12
```{r,label="classifier v12", error=FALSE, message=TRUE, fig.align = "left"}
outV12 <- gb$GetV12score(RGset)
knitr::asis_output(gb$PrintScoreTable(outV12, gb$dat))
```
<a class="molecneuro"></a><hr class="rounded">
### TSNE Clustering Version 11 Classifier (Interactive)
```{r, label='TSNE Cluster', fig.height=7, fig.width=13, out.width ='90%'}
gb$supM(gb$GetClusterPlot(gb$msetDat, gb$dat))
knitr::knit_hooks$set(capture_env = capture_env_hook)
```
<hr class="solid">
### Copy Number Variation Profile Version 11 Classifier (Interactive)
```{r, label='CNV Plot', results='hide'}
cnv11 <- gb$supM(gb$NewGgplotly(gb$msetDat, gb$dat))
```

```{r, label='CNV loss gains table', fig.width = 12, fig.height=7, out.height="500px", results='asis'}
gb$supM(cnv11$thePlot)
gnLss <- cnv11$gainLoss
knitr::asis_output('<p class="cnvdesc"></p> <hr class="dotted"><h4>CNV Gains and Loss</h4>')
if (nrow(gnLss$gainDf) > 0) {knitr::asis_output(gnLss$gainTab)}
if (nrow(gnLss$lossDf) > 0) {knitr::asis_output(gnLss$lossTab)}
```

### Copy Number Variation Profile Version 12
```{r, label="CNV v12", fig.width = 20, fig.height=10, fig.align = "left"}
Mset12 <- mnp.v12b6::MNPpreprocessIllumina(RGset)
mnp.v12b6::MNPcnvplot(Mset12, sex=ifelse(mnp.v12b6::MNPgetSex(Mset12)$predictedSex=="M","Male","Female"), main=gb$dat$sampleID)
```
<p class="conumee"></p><hr class="solid">
### MGMT Status Prediction
```{r, label="mgmtTable", fig.height=1.3, fig.align="left", out.width='40%', results='asis'}
Mset_raw <- minfi::preprocessRaw(RGset)
print(gb$supM(mnp.v12b6::MNPciplot_mgmt(Mset_raw)))
gb$mgmtValues <- gb$GetMgmtPlot(Mset_raw)
knitr::asis_output(gb$mgmtValues$mgmtPlot)
```
<p class="seemgmt"></p><hr class="solid">
### MLH1 Status Prediction 
<div>
```{r, label='MLH1 Prediction', fig.align="left", fig.asp=0.8, fig.width=5, results='asis'}
gb$mlh1Pred <- mlh1Pred <- gb$Mlh1Pipeline(RGset)
print(mlh1Pred$theMlhplot)
knitr::asis_output(mlh1Pred$mlhP)
gb$TryREDCap(gb=globalenv())
```
</div><hr class="hr.dashed">
### UniD Prediction
```{r, label='UniD predict', message=FALSE, results='hide'}
gb$predU <- NULL
tryCatch(
    expr = {
        gb$predU <- gb$supM(gb$PipelineU(sampleID = gb$dat$sampleID, gb$RGset, run_id = gb$dat$run_id))
    },
    error = function(e) {gb$predU <- NULL}
)
```
<p style="font-weight:bold" class="unidcap"></p><p class="unidtxt"></p></br>
```{r, label='UniD output', fig.align="left", results='asis'}
if(!is.null(gb$predU)){
    uniDtabs <- gb$supM(gb$GetUniDTables(gb$predU))
    knitr::asis_output(uniDtabs$tab1)
    knitr::asis_output(uniDtabs$tab2)
    }else{cat("UniD prediction not availible for this sample")}
```
<p class="unidtypes"></p><hr class="dotted"><h4>Reference</h4><a class="naturep"> </a>
<p class="bibrefnames"></p><span><p class="implements"></p></span>
